### 2019-02-24 abstract.tex
first draft

\documentclass{anstrans}

\title{Coupled Neutronics/Thermal-Hydraulics Simulation of the Molten Salt Fast Reactor with Moltres}
\author{Sun Myung Park$^{1,2}$ and Kathryn D. Huff$^1$}
\institute{$^1$Dept. of Nuclear, Plasma and Radiological Engineering, University of Illinois at Urbana-Champaign \\
$^2$smpark3@illinois.edu}

\usepackage{graphicx} % allows inclusion of graphics
\usepackage{booktabs} % nice rules (thick lines) for tables
\usepackage{microtype} % improves typography for PDF
\usepackage{xspace}
\usepackage{multirow} 
\usepackage{array}
\setlength{\arrayrulewidth}{.4mm}
\renewcommand{\arraystretch}{1.2}
\usepackage[labelfont=bf]{caption}
\captionsetup[table]{name=Table}
\renewcommand{\thetable}{\arabic{table}}
\usepackage{subcaption}
\usepackage{enumitem}
\usepackage{placeins}
\usepackage{siunitx}
\newcolumntype{c}{>{\hsize=.56\hsize}X}
\newcolumntype{b}{>{\hsize=.7\hsize}X}
\newcolumntype{s}{>{\hsize=.74\hsize}X}
\newcolumntype{f}{>{\hsize=.1\hsize}X}
\newcolumntype{a}{>{\hsize=.45\hsize}X}
\usepackage{titlesec}
\titleformat*{\subsection}{\normalfont}

\begin{document}

\begin{abstract}
Molten salt reactors (MSR) differ greatly from conventional solid-fuelled reactors, particularly in the neutronics and thermal-hydraulics behaviours. They present unique computational challenges that conventional computational tools fail to address effectively. The development of novel simulation tools for MSRs is an essential step towards understanding the behaviour of MSRs under various conditions. An important requirement for new MSR simulation tools is strong coupling between neutronics and thermal-hydraulics modeling due to the strong temperature reactivity coefficients arising from Doppler effects and changes in the fuel salt density.

Moltres is an open source coupled neutronics/thermal hydraulics simulation tool for simulating MSRs \cite{lindsay_introduction_2018}. It is under active development at the University of Illinois. It is an application code built using the MOOSE finite element framework \cite{gaston_moose:_2009}. Moltres is developed as a solver for the coupled multi-group neutron diffusion, temperature and delayed neutron precursor governing equations. As a multi-group neutronics solver on a coarse mesh, Moltres imposes relatively low computational loads compared to continuous energy neutronics solvers and computational fluid dynamics thermal-hydraulic solvers employed by other researchers in the study of MSRs. This allows for steady-state, transient and accident analyses with relatively low computational requirements.

This abstract presents the outline for the code-to-code verification of Moltres. The reactor model used for this verification is the Molten Salt Fast Reactor. The MSFR is a reference design for a fast-spectrum molten salt reactor developed under the EVOL and SAMOFAR projects\cite{serp_molten_2014}. There is abundant MSFR parameter and simulation data available from various authors \cite{fiorina_modelling_2014} \cite{pettersen_coupled_2016} for the reference model to perform the code-to-code verification.

Moltres requires neutron group constant data from a neutron transport code. For this study, Serpent is used to generate the group constant data. Serpent \cite{leppanen_serpent_2015} is a continuous-energy Monte Carlo code used in numerous reactor physics applications. The inputs consist of MSFR reference model parameters, neutron energy group bounds, a nuclear data library, and the temperatures at which the group constants are to be generated. Six neutron group constant data is generated for the six-group neutron diffusion equation.

Moltres interpolates the provided group constant data generated by Serpent at various discrete temperatures. Other Moltres input parameters include flow velocity, a geometry mesh file, appropriate initial values, boundary conditions and material properties. The flow velocity is essential for advective heat transfer and the movement of delayed neutron precursors in the model.

The full paper will present Moltres results of MSFR reference model under various conditions defined by the reference model, such as the temperature of the fuel at the inlet and outlets and flow velocities. Furthermore, transient scenarios such as pump over-speed will be explored and studied and verified against existing simulation data by various authors.
\end{abstract}

\bibliographystyle{ans}
\bibliography{bibliography}

\end{document}

### 2019-02-27 abstract.tex
second draft

@@
 \usepackage[labelfont=bf]{caption}
-\captionsetup[table]{name=Table}
+%\captionsetup[table]{name=Table}
 \renewcommand{\thetable}{\arabic{table}}
@@
 \newcolumntype{b}{>{\hsize=.7\hsize}X}
-\newcolumntype{s}{>{\hsize=.74\hsize}X}
+%\newcolumntype{s}{>{\hsize=.74\hsize}X}
 \newcolumntype{f}{>{\hsize=.1\hsize}X}
@@
 \begin{abstract}
-Molten salt reactors (MSR) differ greatly from conventional solid-fuelled reactors, particularly in the neutronics and thermal-hydraulics behaviours.
-They present unique computational challenges that conventional computational tools fail to address effectively.
-The development of novel simulation tools for MSRs is an essential step towards understanding the behaviour of MSRs under various conditions.
-An important requirement for new MSR simulation tools is strong coupling between neutronics and thermal-hydraulics modeling due to the strong temperature reactivity coefficients arising from Doppler effects and changes in the fuel salt density.
+%
+This abstract presents the outline for the code-to-code verification of Moltres.
+Moltres \cite{lindsay_introduction_2018} is an open source coupled neutronics/thermal hydraulics simulation tool for simulating molten salt reactors (MSR).
+MSRs differ greatly from conventional solid-fuelled reactors, particularly in their neutronics and thermal-hydraulics behaviours.
+They present unique computational challenges that many existing computational tools fail to address effectively.
+Strong coupling between neutronics and thermal-hydraulics modeling is an important requirement for new MSR simulation tools due to the strong temperature reactivity coefficients arising from Doppler effects and changes in the fuel salt density.
 
-Moltres is an open source coupled neutronics/thermal hydraulics simulation tool for simulating MSRs \cite{lindsay_introduction_2018}.
-It is under active development at the University of Illinois.
-It is an application code built using the MOOSE finite element framework \cite{gaston_moose:_2009}.
+The development of novel simulation tools for MSRs is an essential step towards understanding the behaviour of MSRs under various conditions, one of which is the changing fuel compositions across the lifespan of MSRs.
+The fuel composition in an MSR continuously evolves over time as online refueling replenishes fissile material while removing fission product poisons.
+The impact of changing fuel composition on the safety parameters such as the reactivity feedback coefficient must be studied extensively.
+
+Moltres is an application code built in the MOOSE finite element framework \cite{gaston_moose:_2009}.
 Moltres is developed as a solver for the coupled multi-group neutron diffusion, temperature and delayed neutron precursor governing equations.
-As a multi-group neutronics solver on a coarse mesh, Moltres imposes relatively low computational loads compared to continuous energy neutronics solvers and computational fluid dynamics thermal-hydraulic solvers employed by other researchers in the study of MSRs.
-This allows for steady-state, transient and accident analyses with relatively low computational requirements.
+MOOSE is a parallel framework and it has an adaptive meshing scheme.
+Therefore, reactor simulations with large complex meshes can scale effectively when run on multiple cores.
 
-This abstract presents the outline for the code-to-code verification of Moltres.
-The reactor model used for this verification is the Molten Salt Fast Reactor.
+The Molten Salt Fast Reactor (MSFR) is the MSR model used for the code-to-code verification.
 The MSFR is a reference design for a fast-spectrum molten salt reactor developed under the EVOL and SAMOFAR projects\cite{serp_molten_2014}.
-There is abundant MSFR parameter and simulation data available from various authors \cite{fiorina_modelling_2014} \cite{pettersen_coupled_2016} for the reference model to perform the code-to-code verification.
+There are abundant MSFR parameter and simulation data available from various authors \cite{fiorina_modelling_2014} \cite{pettersen_coupled_2016} for the reference model to perform the code-to-code verification.
 
-Moltres requires neutron group constant data from a neutron transport code.
-For this study, Serpent is used to generate the group constant data.
+The full paper will present Moltres simulation results of the MSFR reference model with three fuel compositions;
+They correspond to start-up, early life and equilibrium fuel compositions.
+The start-up fuel composition is a mix of $^{235}$U and $^{232}$Th in LiF salt.
+This is in line with the main purpose of running the MSFR as a thorium breeder.
+Cross-section data for these fuel compositions will be generated using Serpent.
 Serpent \cite{leppanen_serpent_2015} is a continuous-energy Monte Carlo code used in numerous reactor physics applications.
-The inputs consist of MSFR reference model parameters, neutron energy group bounds, a nuclear data library, and the temperatures at which the group constants are to be generated.
-Six neutron group constant data is generated for the six-group neutron diffusion equation.
+Safety parameters such as reactivity feedback coefficients will be calculated and assessed for the different compositions.
+The results will be compared with simulation data from existing literature.
+[List of authors with start-up and equilibrium fuel composition simulation results].
+Furthermore, transient scenarios such as pump over-speed can be explored.
 
-Moltres interpolates the provided group constant data generated by Serpent at various discrete temperatures.
-Other Moltres input parameters include flow velocity, a geometry mesh file, appropriate initial values, boundary conditions and material properties.
-The flow velocity is essential for advective heat transfer and the movement of delayed neutron precursors in the model.
-
-The full paper will present Moltres results of MSFR reference model under various conditions defined by the reference model, such as the temperature of the fuel at the inlet and outlets and flow velocities.
-Furthermore, transient scenarios such as pump over-speed will be explored and studied and verified against existing simulation data by various authors.
 \end{abstract}
@@
 \end{document}
+\grid

### 2019-02-28 abstract.tex
edit
Second draft edits

@@
 
-\title{Coupled Neutronics/Thermal-Hydraulics Simulation of the Molten Salt Fast Reactor with Moltres}
+\title{Safety Analysis of the Molten Salt Fast Reactor Fuel Composition using Moltres}
 \author{Sun Myung Park$^{1,2}$ and Kathryn D. Huff$^1$}
@@
 %
-This abstract presents the outline for the code-to-code verification of Moltres.
-Moltres \cite{lindsay_introduction_2018} is an open source coupled neutronics/thermal hydraulics simulation tool for simulating molten salt reactors (MSR).
+Molten salt reactors (MSR) potentially possess the ability to run for extended periods with minimal shutdown time due to online fuel reprocessing.
+Their proposed equilibrium fuel compositions differ from start-up compositions due to burnup of initial fissile material, breeding of new fissile material, and production/removal of fission products.
+The impact of changing fuel composition on safety parameters (e.g. reactivity feedback coefficient) must be fully characterized to establish a licensing case for this class of reactors.
+
+Numerous computational tools exist for conventional nuclear reactors.
+However, most are not suitable for the study of MSRs.
 MSRs differ greatly from conventional solid-fuelled reactors, particularly in their neutronics and thermal-hydraulics behaviours.
 They present unique computational challenges that many existing computational tools fail to address effectively.
-Strong coupling between neutronics and thermal-hydraulics modeling is an important requirement for new MSR simulation tools due to the strong temperature reactivity coefficients arising from Doppler effects and changes in the fuel salt density.
+New MSR simulation tools must capture strong coupling between neutronics and thermal-hydraulics exhibited by delayed neutron precursor movement as well as strong Doppler and density feedback in the fuel salt.
+This paper introduces a new simulation tool, Moltres \cite{lindsay_introduction_2018}, for investigating the impact of changing fuel composition on safety parameters.
 
-The development of novel simulation tools for MSRs is an essential step towards understanding the behaviour of MSRs under various conditions, one of which is the changing fuel compositions across the lifespan of MSRs.
-The fuel composition in an MSR continuously evolves over time as online refueling replenishes fissile material while removing fission product poisons.
-The impact of changing fuel composition on the safety parameters such as the reactivity feedback coefficient must be studied extensively.
+Moltres is an open source coupled neutronics/thermal hydraulics simulation tool for simulating MSRs.
+It is a software package built on the MOOSE finite element framework \cite{gaston_moose:_2009}.
+It solves the coupled time-dependent multi-group neutron diffusion, temperature and delayed neutron precursor (DNP) governing equations.
+The temperature and DNP equations fully account for fuel advection as the fuel salt flows upwards through the core.
 
-Moltres is an application code built in the MOOSE finite element framework \cite{gaston_moose:_2009}.
-Moltres is developed as a solver for the coupled multi-group neutron diffusion, temperature and delayed neutron precursor governing equations.
-MOOSE is a parallel framework and it has an adaptive meshing scheme.
-Therefore, reactor simulations with large complex meshes can scale effectively when run on multiple cores.
+The MSR model studied in this paper is the Molten Salt Fast Reactor (MSFR) \cite{merle-lucotte_launching_2011}.
+The MSFR is a reference design for a fast-spectrum molten salt reactor developed under the EVOL and SAMOFAR projects \cite{serp_molten_2014}.
 
-The Molten Salt Fast Reactor (MSFR) is the MSR model used for the code-to-code verification.
-The MSFR is a reference design for a fast-spectrum molten salt reactor developed under the EVOL and SAMOFAR projects\cite{serp_molten_2014}.
-There are abundant MSFR parameter and simulation data available from various authors \cite{fiorina_modelling_2014} \cite{pettersen_coupled_2016} for the reference model to perform the code-to-code verification.
-
-The full paper will present Moltres simulation results of the MSFR reference model with three fuel compositions;
-They correspond to start-up, early life and equilibrium fuel compositions.
-The start-up fuel composition is a mix of $^{235}$U and $^{232}$Th in LiF salt.
+The full paper will present Moltres simulation results of the MSFR reference model with three fuel compositions:
+start-up, early life and equilibrium fuel compositions.
+The chosen start-up fuel composition is a eutectic mixture of $^{233}$U and $^{232}$Th fluorides in a lithium fluoride molten salt \cite{merle-lucotte_launching_2011}.
 This is in line with the main purpose of running the MSFR as a thorium breeder.
-Cross-section data for these fuel compositions will be generated using Serpent.
-Serpent \cite{leppanen_serpent_2015} is a continuous-energy Monte Carlo code used in numerous reactor physics applications.
-Safety parameters such as reactivity feedback coefficients will be calculated and assessed for the different compositions.
-The results will be compared with simulation data from existing literature.
-[List of authors with start-up and equilibrium fuel composition simulation results].
-Furthermore, transient scenarios such as pump over-speed can be explored.
+Cross-section data for these fuel compositions are generated using Serpent \cite{leppanen_serpent_2015},
+which is a continuous-energy Monte Carlo code used in numerous reactor physics applications.
+Moltres will solve the coupled neutron transport equation as a steady-state eigenvalue problem to obtain the effective neutron multiplication factor, $k_{eff}$.
+For each fuel composition, the temperature distribution and densities will be varied slightly from the steady-state configuration to obtain the change in $k_{eff}$.
+Reactivity feedback coefficients will be calculated from these variations and assessed for each fuel compositions.
+Finally, the results will be compared with existing data \cite{fiorina_analysis_2012} \cite{fiorina_investigation_2013} of safety parameters for the three fuel compositions.
 
@@
 \end{document}
-\grid

### 2019-03-15 abstract.tex

@@
 
+\usepackage[acronym,toc]{glossaries}
+\include{acros}
+\makeglossaries
+
 \begin{document}
@@
 %
-Molten salt reactors (MSR) potentially possess the ability to run for extended periods with minimal shutdown time due to online fuel reprocessing.
-Their proposed equilibrium fuel compositions differ from start-up compositions due to burnup of initial fissile material, breeding of new fissile material, and production/removal of fission products.
-The impact of changing fuel composition on safety parameters (e.g. reactivity feedback coefficient) must be fully characterized to establish a licensing case for this class of reactors.
+        \glspl{MSR} potentially possess the ability to run for extended 
+        periods with minimal shutdown time due to online fuel reprocessing.  
+        Their proposed equilibrium fuel compositions differ substantially from 
+        start-up compositions due to burnup of initial fissile material and 
+        breeding of new fissile material, but also fissile material feeds and 
+        removal of fission products.  Since the changing fuel composition 
+        impacts safety parameters (e.g. reactivity feedback coefficients), a 
+        licensing case for this class of reactors  must fully characterize 
+        those impacts.
 
-Numerous computational tools exist for conventional nuclear reactors.
-However, most are not suitable for the study of MSRs.
-MSRs differ greatly from conventional solid-fuelled reactors, particularly in their neutronics and thermal-hydraulics behaviours.
-They present unique computational challenges that many existing computational tools fail to address effectively.
-New MSR simulation tools must capture strong coupling between neutronics and thermal-hydraulics exhibited by delayed neutron precursor movement as well as strong Doppler and density feedback in the fuel salt.
-This paper introduces a new simulation tool, Moltres \cite{lindsay_introduction_2018}, for investigating the impact of changing fuel composition on safety parameters.
+Numerous computational tools exist for conventional nuclear reactors, but 
+        \glspl{MSR} present unique computational challenges that many fail to 
+        address effectively.  \glspl{MSR} differ profoundly from conventional 
+        solid-fuelled reactors, particularly in their neutronics and 
+        thermal-hydraulics behaviors.  New \gls{MSR} simulation tools must 
+        capture strong coupling between neutronics and thermal-hydraulics 
+        exhibited by delayed neutron precursor movement as well as strong 
+        Doppler and density feedback in the fuel salt.  This paper investigates 
+        the impact of changing fuel composition on safety parameters in the 
+        \gls{MSFR}  using a new simulation tool for \glspl{MSR}, Moltres 
+        \cite{lindsay_introduction_2018}.
 
-Moltres is an open source coupled neutronics/thermal hydraulics simulation tool for simulating MSRs.
-It is a software package built on the MOOSE finite element framework \cite{gaston_moose:_2009}.
-It solves the coupled time-dependent multi-group neutron diffusion, temperature and delayed neutron precursor (DNP) governing equations.
-The temperature and DNP equations fully account for fuel advection as the fuel salt flows upwards through the core.
+Moltres is an open source coupled neutronics/thermal hydraulics simulation 
+        application for simulating \glspl{MSR}. Built on the \gls{MOOSE} finite 
+        element framework \cite{gaston_moose:_2009}, Moltres solves the coupled 
+        time-dependent multi-group neutron diffusion, temperature, and 
+        \gls{DNP} governing equations.  The temperature and DNP equations fully 
+        account for fuel advection as the fuel salt flows upwards through the 
+        core.
 
-The MSR model studied in this paper is the Molten Salt Fast Reactor (MSFR) \cite{merle-lucotte_launching_2011}.
-The MSFR is a reference design for a fast-spectrum molten salt reactor developed under the EVOL and SAMOFAR projects \cite{serp_molten_2014}.
+The \gls{MSFR} model studied in this paper
+        \cite{merle-lucotte_launching_2011}, is a reference design for a 
+        fast-spectrum \gls{MSR} developed under the \gls{EVOL} and 
+        \gls{SAMOFAR} projects \cite{serp_molten_2014}.
+        The full paper will present results from Moltres simulation of the 
+        \gls{MSFR} reference model with three fuel compositions:
+        start-up, early life, and equilibrium.
 
-The full paper will present Moltres simulation results of the MSFR reference model with three fuel compositions:
-start-up, early life and equilibrium fuel compositions.
-The chosen start-up fuel composition is a eutectic mixture of $^{233}$U and $^{232}$Th fluorides in a lithium fluoride molten salt \cite{merle-lucotte_launching_2011}.
-This is in line with the main purpose of running the MSFR as a thorium breeder.
-Cross-section data for these fuel compositions are generated using Serpent \cite{leppanen_serpent_2015},
-which is a continuous-energy Monte Carlo code used in numerous reactor physics applications.
-Moltres will solve the coupled neutron transport equation as a steady-state eigenvalue problem to obtain the effective neutron multiplication factor, $k_{eff}$.
-For each fuel composition, the temperature distribution and densities will be varied slightly from the steady-state configuration to obtain the change in $k_{eff}$.
-Reactivity feedback coefficients will be calculated from these variations and assessed for each fuel compositions.
-Finally, the results will be compared with existing data \cite{fiorina_analysis_2012} \cite{fiorina_investigation_2013} of safety parameters for the three fuel compositions.
-
+In line with the purpose of the \gls{MSFR} as a thorium breeder, its chosen 
+        start-up fuel composition is a eutectic mixture of $^{233}$U and 
+        $^{232}$Th fluorides in a lithium fluoride molten salt 
+        \cite{merle-lucotte_launching_2011}. We generate group constants for 
+        each fuel composition using Serpent \cite{leppanen_serpent_2015}, a 
+        continuous-energy Monte Carlo code used in numerous reactor physics 
+        applications. For verification, group constants and reactivity 
+        coefficients will be compared with existing data 
+        \cite{fiorina_analysis_2012,fiorina_investigation_2013} of safety 
+        parameters for the three fuel compositions.  
+        Using these group constants ($\chi$, $\nu\Sigma_f$, 
+        $\Sigma_{g\rightarrow g'}$, $\frac{d\rho}{dT}$, etc.), Moltres then 
+        solves for the flux and temperature based on the neutron diffusion 
+        equation coupled with navier stokes thermal hydraulics. Transient 
+        simulations will establish the spatial distribution of flux, 
+        $\phi_g(\vec{r})$ and temperature, $T(\vec{r})$ during transients.
 \end{abstract}

### 2019-03-15 abstract.tex
final edits

@@
         each fuel composition using Serpent \cite{leppanen_serpent_2015}, a 
-        continuous-energy Monte Carlo code used in numerous reactor physics 
-        applications. For verification, group constants and reactivity 
-        coefficients will be compared with existing data 
+        continuous-energy Monte Carlo code for numerous reactor physics 
+        applications. For verification, we will compare group constants and
+        reactivity coefficients with existing data 
         \cite{fiorina_analysis_2012,fiorina_investigation_2013} of safety 
@@
         $\phi_g(\vec{r})$ and temperature, $T(\vec{r})$ during transients.
+        These distributions will give insight into MSFR behavior during
+        transients, and identify potential risks that may warrant further
+        study and changes to the fuel composition or the online fuel
+        reprocessing scheme.
 \end{abstract}

### 2019-03-15 abstract.tex
final final edits

@@
         $\phi_g(\vec{r})$ and temperature, $T(\vec{r})$ during transients.
-        These distributions will give insight into MSFR behavior during
-        transients, and identify potential risks that may warrant further
-        study and changes to the fuel composition or the online fuel
-        reprocessing scheme.
+        These distributions will give insight into MSFR transient behavior,
+        which will help us identify potential safety risks.
+        These risks may warrant further study and possibly, changes to the
+        fuel composition or the online fuel reprocessing scheme.
 \end{abstract}

### 2019-06-16 abstract/acros.tex
full paper first draft

%\newacronym{<++>}{<++>}{<++>}
\newacronym[longplural={metric tons of heavy metal}]{MTHM}{MTHM}{metric ton of heavy metal}
\newacronym{ABM}{ABM}{agent-based modeling}
\newacronym{ACDIS}{ACDIS}{Program in Arms Control \& Domestic and International Security}
\newacronym{AHTR}{AHTR}{Advanced High Temperature Reactor}
\newacronym{ANDRA}{ANDRA}{Agence Nationale pour la gestion des D\'echets RAdioactifs, the French National Agency for Radioactive Waste Management}
\newacronym{ANL}{ANL}{Argonne National Laboratory}
\newacronym{API}{API}{application programming interface}
\newacronym{ARE}{ARE}{Aircraft Reactor Experiment}
\newacronym{ASME}{ASME}{American Society of Mechanical Engineers}
\newacronym{ATWS}{ATWS}{Anticipated Transient Without Scram}
\newacronym{BDBE}{BDBE}{Beyond Design Basis Event}
\newacronym{BIDS}{BIDS}{Berkeley Institute for Data Science}
\newacronym{CAFCA}{CAFCA}{ Code for Advanced Fuel Cycles Assessment }
\newacronym{CDTN}{CDTN}{Centro de Desenvolvimento da Tecnologia Nuclear}
\newacronym{CEA}{CEA}{Commissariat \`a l'\'Energie Atomique et aux \'Energies Alternatives}
\newacronym{CFD}{CFD}{Computational Fluid Dynamics}
\newacronym{CI}{CI}{continuous integration}
\newacronym{CNEN}{CNEN}{Comiss\~{a}o Nacional de Energia Nuclear}
\newacronym{CNERG}{CNERG}{Computational Nuclear Engineering Research Group}
\newacronym{COMSOL}{COMSOL}{COMmon SOLution}
\newacronym{COSI}{COSI}{Commelini-Sicard}
\newacronym{COTS}{COTS}{commercial, off-the-shelf}
\newacronym{CSNF}{CSNF}{commercial spent nuclear fuel}
\newacronym{CTAH}{CTAHs}{Coiled Tube Air Heaters}
\newacronym{CUBIT}{CUBIT}{CUBIT Geometry and Mesh Generation Toolkit}
\newacronym{CURIE}{CURIE}{Centralized Used Fuel Resource for Information Exchange}
\newacronym{DAG}{DAG}{directed acyclic graph}
\newacronym{DANESS}{DANESS}{Dynamic Analysis of Nuclear Energy System Strategies}
\newacronym{DBE}{DBE}{Design Basis Event}
\newacronym{DESAE}{DESAE}{Dynamic Analysis of Nuclear Energy Systems Strategies}
\newacronym{DHS}{DHS}{Department of Homeland Security}
\newacronym{DNP}{DNP}{delayed neutron precursor}
\newacronym{DOE}{DOE}{Department of Energy}
\newacronym{DRACS}{DRACS}{Direct Reactor Auxiliary Cooling System}
\newacronym{DRE}{DRE}{dynamic resource exchange}
\newacronym{DSNF}{DSNF}{DOE spent nuclear fuel}
\newacronym{DYMOND}{DYMOND}{Dynamic Model of Nuclear Development }
\newacronym{EBS}{EBS}{Engineered Barrier System}
\newacronym{EDZ}{EDZ}{Excavation Disturbed Zone}
\newacronym{EPA}{EPA}{Environmental Protection Agency}
\newacronym{EP}{EP}{Engineering Physics}
\newacronym{EVOL}{EVOL}{Evaluation and Viability of Liquid Fuel Fast Reactor System}
\newacronym{FCO}{FCO}{Fuel Cycle Options}
\newacronym{FCT}{FCT}{Fuel Cycle Technology}
\newacronym{FEHM}{FEHM}{Finite Element Heat and Mass Transfer}
\newacronym{FEPs}{FEPs}{Features, Events, and Processes}
\newacronym{FHR}{FHR}{Fluoride-Salt-Cooled High-Temperature Reactor}
\newacronym{FLiBe}{FLiBe}{Fluoride-Lithium-Beryllium}
\newacronym{GDSE}{GDSE}{Generic Disposal System Environment}
\newacronym{GDSM}{GDSM}{Generic Disposal System Model}
\newacronym{GENIUSv1}{GENIUSv1}{Global Evaluation of Nuclear Infrastructure Utilization Scenarios, Version 1}
\newacronym{GENIUSv2}{GENIUSv2}{Global Evaluation of Nuclear Infrastructure Utilization Scenarios, Version 2}
\newacronym{GENIUS}{GENIUS}{Global Evaluation of Nuclear Infrastructure Utilization Scenarios}
\newacronym{GPAM}{GPAM}{Generic Performance Assessment Model}
\newacronym{GRSAC}{GRSAC}{Graphite Reactor Severe Accident Code}
\newacronym{GUI}{GUI}{graphical user interface}
\newacronym{HLW}{HLW}{high level waste}
\newacronym{HPC}{HPC}{high-performance computing}
\newacronym{HTC}{HTC}{high-throughput computing}
\newacronym{HTGR}{HTGR}{High Temperature Gas-Cooled Reactor}
\newacronym{IAEA}{IAEA}{International Atomic Energy Agency}
\newacronym{IEMA}{IEMA}{Illinois Emergency Mangament Agency}
\newacronym{IHLRWM}{IHLRWM}{International High Level Radioactive Waste Management}
\newacronym{INL}{INL}{Idaho National Laboratory}
\newacronym{IPRR1}{IRP-R1}{Instituto de Pesquisas Radioativas Reator 1}
\newacronym{IRP}{IRP}{Integrated Research Project}
\newacronym{ISFSI}{ISFSI}{Independent Spent Fuel Storage Installation}
\newacronym{ISRG}{ISRG}{Independent Student Research Group}
\newacronym{JFNK}{JFNK}{Jacobian-Free Newton Krylov}
\newacronym{LANL}{LANL}{Los Alamos National Laboratory}
\newacronym{LBNL}{LBNL}{Lawrence Berkeley National Laboratory}
\newacronym{LCOE}{LCOE}{levelized cost of electricity}
\newacronym{LDRD}{LDRD}{laboratory directed research and development}
\newacronym{LFR}{LFR}{Lead-Cooled Fast Reactor}
\newacronym{LLNL}{LLNL}{Lawrence Livermore National Laboratory}
\newacronym{LMFBR}{LMFBR}{Liquid Metal Fast Breeder Reactor}
\newacronym{LOFC}{LOFC}{Loss of Forced Cooling}
\newacronym{LOHS}{LOHS}{Loss of Heat Sink}
\newacronym{LOLA}{LOLA}{Loss of Large Area}
\newacronym{LP}{LP}{linear program}
\newacronym{LWR}{LWR}{Light Water Reactor}
\newacronym{MAGNOX}{MAGNOX}{Magnesium Alloy Graphie Moderated Gas Cooled Uranium Oxide Reactor}
\newacronym{MA}{MA}{minor actinide}
\newacronym{MCNP}{MCNP}{Monte Carlo N-Particle code}
\newacronym{MILP}{MILP}{mixed-integer linear program}
\newacronym{MIT}{MIT}{the Massachusetts Institute of Technology}
\newacronym{MOAB}{MOAB}{Mesh-Oriented datABase}
\newacronym{MOOSE}{MOOSE}{Multiphysics Object-Oriented Simulation Environment}
\newacronym{MOSART}{MOSART}{Molten Salt Actinide Recycler and Transmuter}
\newacronym{MOX}{MOX}{mixed oxide}
\newacronym{MPI}{MPI}{Message Passing Interface}
\newacronym{MRPP}{MRPP}{Multiregion Processing Plant}
\newacronym{MSBR}{MSBR}{Molten Salt Breeder Reactor}
\newacronym{MSFR}{MSFR}{Molten Salt Fast Reactor}
\newacronym{MSRE}{MSRE}{Molten Salt Reactor Experiment}
\newacronym{MSR}{MSR}{Molten Salt Reactor}
\newacronym{NAGRA}{NAGRA}{National Cooperative for the Disposal of Radioactive Waste}
\newacronym{NEAMS}{NEAMS}{Nuclear Energy Advanced Modeling and Simulation}
\newacronym{NEUP}{NEUP}{Nuclear Energy University Programs}
\newacronym{NFCSim}{NFCSim}{Nuclear Fuel Cycle Simulator}
\newacronym{NGNP}{NGNP}{Next Generation Nuclear Plant}
\newacronym{NMWPC}{NMWPC}{Nuclear MW Per Capita}
\newacronym{NNSA}{NNSA}{National Nuclear Security Administration}
\newacronym{NPP}{NPP}{Nuclear Power Plant}
\newacronym{NPRE}{NPRE}{Department of Nuclear, Plasma, and Radiological Engineering}
\newacronym{NQA1}{NQA-1}{Nuclear Quality Assurance - 1}
\newacronym{NRC}{NRC}{Nuclear Regulatory Commission}
\newacronym{NSF}{NSF}{National Science Foundation}
\newacronym{NSSC}{NSSC}{Nuclear Science and Security Consortium}
\newacronym{NUWASTE}{NUWASTE}{Nuclear Waste Assessment System for Technical Evaluation}
\newacronym{NWF}{NWF}{Nuclear Waste Fund}
\newacronym{NWTRB}{NWTRB}{Nuclear Waste Technical Review Board}
\newacronym{OCRWM}{OCRWM}{Office of Civilian Radioactive Waste Management}
\newacronym{ORION}{ORION}{ORION}
\newacronym{ORNL}{ORNL}{Oak Ridge National Laboratory}
\newacronym{PARCS}{PARCS}{Purdue Advanced Reactor Core Simulator}
\newacronym{PBAHTR}{PB-AHTR}{Pebble Bed Advanced High Temperature Reactor}
\newacronym{PBFHR}{PB-FHR}{Pebble-Bed Fluoride-Salt-Cooled High-Temperature Reactor}
\newacronym{PDE}{PDE}{partial differential equation}
\newacronym{PEI}{PEI}{Peak Environmental Impact}
\newacronym{PH}{PRONGHORN}{PRONGHORN}
\newacronym{PRIS}{PRIS}{Power Reactor Information System}
\newacronym{PRKE}{PRKE}{Point Reactor Kinetics Equations}
\newacronym{PSPG}{PSPG}{Pressure-Stabilizing/Petrov-Galerkin}
\newacronym{PWAR}{PWAR}{Pratt and Whitney Aircraft Reactor}
\newacronym{PWR}{PWR}{Pressurized Water Reactor}
\newacronym{PyNE}{PyNE}{Python toolkit for Nuclear Engineering}
\newacronym{PyRK}{PyRK}{Python for Reactor Kinetics}
\newacronym{QA}{QA}{quality assurance}
\newacronym{RDD}{RD\&D}{Research Development and Demonstration}
\newacronym{RD}{R\&D}{Research and Development}
\newacronym{REE}{REE}{rare earth element}
\newacronym{RELAP}{RELAP}{Reactor Excursion and Leak Analysis Program}
\newacronym{RIA}{RIA}{Reactivity Insertion Accident}
\newacronym{RIF}{RIF}{Region-Institution-Facility}
\newacronym{ROD}{ROD}{Reactor Optimum Design}
\newacronym{SAMOFAR}{SAMOFAR}{Safety Assessment of the Molten Salt Fast Reactor}
\newacronym{SAM}{SAM}{System Analysis Module}
\newacronym{SFR}{SFR}{Sodium-Cooled Fast Reactor}
\newacronym{SINDAG}{SINDA{\textbackslash}G}{Systems Improved Numerical Differencing Analyzer $\backslash$ Gaski}
\newacronym{SKB}{SKB}{Svensk K\"{a}rnbr\"{a}nslehantering AB}
\newacronym{SNF}{SNF}{spent nuclear fuel}
\newacronym{SNL}{SNL}{Sandia National Laboratory}
\newacronym{STC}{STC}{specific temperature change}
\newacronym{SUPG}{SUPG}{Streamline-Upwind/Petrov-Galerkin}
\newacronym{SWF}{SWF}{Separations and Waste Forms}
\newacronym{SWU}{SWU}{Separative Work Unit}
\newacronym{TRIGA}{TRIGA}{Training Research Isotope General Atomic}
\newacronym{TRISO}{TRISO}{Tristructural Isotropic}
\newacronym{TSM}{TSM}{Total System Model}
\newacronym{TSPA}{TSPA}{Total System Performance Assessment for the Yucca Mountain License Application}
\newacronym{ThOX}{ThOX}{thorium oxide}
\newacronym{UFD}{UFD}{Used Fuel Disposition}
\newacronym{UML}{UML}{Unified Modeling Language}
\newacronym{UOX}{UOX}{uranium oxide}
\newacronym{UQ}{UQ}{uncertainty quantification}
\newacronym{US}{US}{United States}
\newacronym{UW}{UW}{University of Wisconsin}
\newacronym{VISION}{VISION}{the Verifiable Fuel Cycle Simulation Model}
\newacronym{VVER}{VVER}{Voda-Vodyanoi Energetichesky Reaktor (Russian Pressurized Water Reactor)}
\newacronym{VV}{V\&V}{verification and validation}
\newacronym{WIPP}{WIPP}{Waste Isolation Pilot Plant}
\newacronym{YMR}{YMR}{Yucca Mountain Repository Site}

### 2019-06-16 paper/paper.tex
full paper first draft

\documentclass{anstrans}

\title{Safety Analysis of the Molten Salt Fast Reactor Fuel Composition using Moltres}
\author{Sun Myung Park$^{a,b}$, Andrei Rykhlevskii$^a$, and Kathryn D. Huff$^a$}
\institute{$^a$Dept. of Nuclear, Plasma and Radiological Engineering, University of Illinois at Urbana-Champaign \\
$^b$smpark3@illinois.edu}

\usepackage{graphicx} % allows inclusion of graphics
\usepackage{booktabs} % nice rules (thick lines) for tables
\usepackage{microtype} % improves typography for PDF
\usepackage{float}
\usepackage{longtable}
\usepackage{xspace}
\usepackage{multirow} 
\usepackage{array}
\setlength{\arrayrulewidth}{.4mm}
\renewcommand{\arraystretch}{1.2}
\usepackage[labelfont=bf]{caption}
%\captionsetup[table]{name=Table}
\renewcommand{\thetable}{\arabic{table}}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{enumitem}
\usepackage{placeins}
\usepackage{siunitx}
\newcolumntype{c}{>{\hsize=.56\hsize}X}
\newcolumntype{b}{>{\hsize=.7\hsize}X}
%\newcolumntype{s}{>{\hsize=.74\hsize}X}
\newcolumntype{f}{>{\hsize=.1\hsize}X}
\newcolumntype{a}{>{\hsize=.45\hsize}X}
\usepackage{titlesec}
\titleformat*{\subsection}{\normalfont}
\usepackage[super]{cite}
\usepackage{multirow}
\usepackage{hhline}

\usepackage[acronym,toc]{glossaries}
\include{acros}
\makeglossaries

\begin{document}

\begin{abstract}
%
    Abstract
\end{abstract}

\section{Introduction}

	\glspl{MSR} are a class of nuclear reactors that
	contain nuclear fuel dissolved and circulating in a molten salt coolant
	loop.
	They potentially possess the ability to run for extended 
    periods with minimal shutdown time due to online fuel reprocessing, which
    is a clear advantage over solid-fuelled reactors that require significant
    downtime for refuelling.
    Their proposed equilibrium fuel compositions differ substantially from
    start-up compositions due to burnup of initial fissile material and 
    breeding of new fissile material, but also fissile material feeds and 
    removal of fission products. Also, while \gls{BOL} fuel composition is
    largely dependent on the initial core loading, the long-term equilibrium
    fuel composition is determined by the type of feed.
    Since the changing fuel composition 
    impacts safety parameters (e.g. reactivity feedback coefficients), a 
    licensing case for this class of reactors  must fully characterize 
    those impacts.

	While numerous computational tools exist for conventional nuclear reactors, 
    \glspl{MSR} present unique computational challenges that many fail to 
    address effectively. \glspl{MSR} differ
    profoundly from conventional 
    solid-fuelled reactors, particularly in their neutronics and 
    thermal-hydraulics behaviors.  New \gls{MSR} simulation tools must 
    capture strong coupling between neutronics and thermal-hydraulics 
    exhibited by \gls{DNP} movement as well as strong 
    Doppler and density feedback in the fuel salt.  This paper investigates 
    the impact of changing fuel composition on safety parameters in the 
    \gls{MSFR} concept using a new simulation tool for \glspl{MSR}, Moltres 
    \cite{lindsay_introduction_2018}.

    Moltres is an open source coupled neutronics/thermal hydraulics simulation 
    application for simulating \glspl{MSR}. Built on the \gls{MOOSE} finite 
    element framework \cite{gaston_moose:_2009}, Moltres solves the coupled 
    time-dependent multi-group neutron diffusion, temperature, and 
    \gls{DNP} governing equations.  The temperature and \gls{DNP} equations
    fully 
    account for fuel advection as the fuel salt flows upwards through the 
    core.

    The \gls{MSFR} model studied in this paper is a reference design for a 
    fast-spectrum \gls{MSR} developed under H2020
    \gls{SAMOFAR} project \cite{serp_molten_2014} (cite gerardin instead).
    The \gls{MSFR} boasts several safety and sustainability advantages over
    conventional reactors. Firstly, it can run on a closed thorium fuel cycle,
    which reduces actinide production and waste radiotoxity.
    The fast neutron spectrum improves $^{233}$U breeding from $^{232}$Th, an
    isotope that is about three times as abundant as uranium.
    Lastly, the \gls{MSFR} operates at near atmospheric pressure; this reduces
    the risk of containment structure failure and manufacturing costs.

    This paper presents results from Moltres simulations of the 
    \gls{MSFR} reference model with three fuel compositions:
    start-up, \gls{BOL}, and equilibrium. In line with the purpose of the
    \gls{MSFR} as a thorium breeder, the chosen start-up fuel composition
    under study is a eutectic mixture of $^{233}$U and 
    $^{232}$Th fluorides in a lithium fluoride molten salt 
    \cite{merle-lucotte_launching_2011}, with
    a Th/$^{233}$U mixture feed. $^{233}$U is extracted from
    the blanket tank and reinserted into the core.

    We generated group constants for 
    each fuel composition using SERPENT \cite{leppanen_serpent_2015}, a 
    continuous-energy Monte Carlo code for numerous reactor physics 
    applications. For verification, we will compare group constants and
    reactivity coefficients with existing data 
    \cite{fiorina_analysis_2012,fiorina_investigation_2013} of safety 
    parameters for the three fuel compositions.  
    Using these group constants ($\chi$, $\nu\Sigma_f$, 
    $\Sigma_{g\rightarrow g'}$, $\frac{d\rho}{dT}$, etc.), Moltres then 
    solves for the flux and temperature based on the neutron diffusion 
    equation coupled with navier stokes thermal hydraulics. Transient 
    simulations will establish the spatial distribution of flux, 
    $\phi_g(\vec{r})$ and temperature, $T(\vec{r})$ during transients.
    These distributions will give insight into MSFR transient behavior,
    which will help us identify potential safety risks.
    These risks may warrant further study and possibly, changes to the
    fuel composition or the online fuel reprocessing scheme.

\section{Molten Salt Fast Reactor}

	The \gls{MSFR} is a reference design for a fast-spectrum molten salt
	reactor
	first developed under the \gls{EVOL} project, and continued by the
	\gls{SAMOFAR} project \cite{serp_molten_2014}.
	Figure \ref{fig:msfr} shows a schematic view of the \gls{MSFR}. The main
	specifications of the \gls{MSFR} are given in Table \ref{table:msfr}.

	Lithium fluoride (LiF) is the major component of the fuel and blanket
	molten salts used for the \gls{MSFR}. Fissile and fertile isotopes are
	introduced
	into the mixture by mole fractions of 77.5\%LiF-22.5\%AcF$_4$, where
	AcF$_4$ represents actinide fluorides such as uranium and thorium
	fluorides.
	The \gls{MSFR} supports various fuel compositions. It can run on the same 
	$^{235}$U-$^{238}$U fuel used in most conventional LWRs. It can also run
	on a
	mixture of fresh and used uranium fuel containing reprocessed TRU
	isotopes \cite{fiorina_investigation_2013}. However, the main configuration
	of the \gls{MSFR} is a breeder reactor running on $^{233}$U-$^{232}$Th
	\cite{merle-lucotte_launching_2011}. Previous studies have reported
	breeding ratios of up to 1.1 on the \gls{MSFR} \cite{fiorina_molten_2013}.

\begin{figure}[t] 
	\centering
	\includegraphics[width=0.48\textwidth]{./figures/MSFR}
	\caption{MSFR reactor design concept \cite{serp_molten_2014}.}
	\label{fig:msfr}
\end{figure}

\begin{table}[t]
	\caption{Specifications of the \gls{MSFR} design \cite{serp_molten_2014}.}
	\begin{tabular}{ l l }
		\hline
		Parameter & Value \\
		\hline
		Thermal/Electric output [MW$_{\text{th}}$/MW$_{\text{e}}$] & 3000 /
		1500 
		\\
		Salt volume [m$^3$] & 18 \\
		Salt fraction in core & 0.5 \\
		Number of circulation loops & 16 \\
		Nominal flow rate [kg s$^{-1}$] & 18500  \\
		Nominal circulation time [s] & 4.0 \\
		Inlet/outlet temperature [K] & 923 / 1023 \\
		Blanket volume [m$^3$] & 7.3\\
		\hline
	\end{tabular}
	\label{table:msfr}
\end{table}

	The primary fuel salt flows upwards through the 9 m$^3$ central core
	region. At the top of the core, the flow separates into 16 smaller external
	loops, each of which passes through a heat exchanger and is pumped back
	into the core. The primary heat exchangers transfer heat from the fuel salt 
	to an intermediate salt coolant loop. There are other instrumentation along
	the external loops for online reprocessing and gas sparging. The core is
	radially surrounded by a tank of blanket molten salt, with reflectors at
	the top and bottom of the core. The blanket salt contains fertile isotopes
	such as $^{232}$Th for fuel breeding. There is a layer of neutron absorbing
	material behind the blanket tanks to protect the heat exchangers, pumps and
	other instrumentation from neutron irradiation damage.

	Various authors have performed a number of steady state and transient
	multiphysics simulations for the \gls{MSFR}. A paper by Fiorina et al.
	\cite{fiorina_modelling_2014} compares results between coupled models
	developed on the multiphysics code COMSOL and an in-house code developed at
	Delft University of Technology. The models used 2D axisymmetric models of
	the \gls{MSFR} and solved multi-group neutron diffusion equations for the
	neutronics, and they showed good agreement for some of the transient cases
	studied. A more comprehensive 3D model has been developed and studied by
	Aufiero et al. \cite{aufiero_development_2014} using the computional fluid
	dynamics (CFD) toolbox OpenFOAM. Although this model relied on the one
	group neutron diffusion equation, it enabled the study of the full 3D core
	geometry and 3D transient scenarios such as the failure of one of the 16
	pumps in the \gls{MSFR}.

	More recently, a coupled tool, comprising of the thermal-hydraulics code
	TRACE and a multi-group 3D spatial neutronics solver \gls{PARCS}, was
	used to run steady state and transient simulations of the \gls{MSFR}
	\cite{pettersen_coupled_2016}. This approach allowed for a 3D model
	simulation of the \gls{MSFR} on a coarse mesh, thus improving on the 2D
	axisymmetric COMSOL/TUDelft models with the benefit of much lower
	computation times in comparison to the CFD-OpenFOAM models. On top of
	steady state simulations, the transient scenarios studied by Pettersen
	\cite{pettersen_coupled_2016} include loss of heat sink, pump over-speed,
	over-cooling and loss of flow.

\section{Methodology}

	This section describes the overall modelling approach and the codes used
	in this paper. First, the \gls{BOL} and equilibrium compositions were
	obtained from SCALE/TRITON unit cell depletion calculations by Rykhlevskii
	et al. (cite Andrei) Their paper used a unit cell model for the modelling
	fuel cycle performance of the \gls{MSFR} and three other fast-spectrum
	\glspl{MSR}. The neutron spectrum and depletion calculations on the unit
	cell SCALE/TRITON models were verified against full core SERPENT models and
	showed very good agreement. The equilibrium composition was selected at
	approximately 43 years after start-up because the TRU vector change
	between each depletion time-step from this moment onwards is less than 3\%.
	(cite Andrei) For the \gls{BOL} composition, it is the fuel composition at
	300 days after start-up. Decay isotopes, whose neutron cross-section data
	are not found in the
	JEFF-3.1.2 nuclear data library, were omitted.

	Neutronics calculations were performed on SERPENT using these fuel
	compositions and a truncated, reference \gls{MSFR} core model
	\cite{pettersen_coupled_2016} to generate six-group neutronics data for
	Moltres.
	The energy boundaries for the six neutron groups are adopted from previous
	\gls{MSFR} studies and shown in Table \ref{table:bound}.
	As for the \gls{DNP} groups, there are eight groups as defined by the
	JEFF-3.1.2 nuclear data library used for neutron cross-section data.
	The reactor model is a 2D axisymmetric model as shown in
	Figure \ref{fig:reference}. This geometry focuses on the active central
	region of the core. Basing the geometry on the reference model facilitates
	comparisons with previous MSFR studies by various authors
	\cite{fiorina_modelling_2014} \cite{pettersen_coupled_2016} on the
	reference model for code-to-code verification purposes.
	The 2D model is extended into a 3D model in SERPENT by rotating it
	around the central axis to form concentric cylinders.

\begin{table}[b]
	\centering
	\captionsetup{justification=centering}
	\caption{Neutron energy group upper bounds used in Serpent.}
	\begin{tabular}{ll}
		\hline
		{Group number} & {Upper bound [MeV]}\\
		\hline
		1 & 7.485$\times 10^{-4}$\\
		2 & 5.5308$\times 10^{-3}$\\
		3 & 2.47875$\times 10^{-2}$\\
		4 & 0.4979\\
		5 & 2.2313\\
		6 & 12\\
		\hline
	\end{tabular}
	\label{table:bound}
\end{table}

	Finally, with the group constant data from SERPENT, Moltres
	calculated the resulting coupled neutron spectrum and temperature
	distribution for a given velocity profile in the core, from user-specified
	initial conditions towards steady state, or from steady state in the case
	of an accident scenario. The mesh geometry for Moltres is
	further simplified from the SERPENT model by the omission of the absorber,
	heat exchanger, and reflector regions. This is justified as they have
	negligible contribution towards the neutronics. Instead, a vacuum
	boundary condition was imposed on the outer surface of the blanket region,
	along with 923 K Dirichlet boundary conditions for temperature.
	The 2 cm thick blanket tank structural material was also omitted as its
	inclusion resulted in an extra fine mesh which drastically
	increased computational time. (Insert Moltres mesh model)

	Moltres has a loop app functionality to account for the flow and decay of
	\glspl{DNP} outside the active core region. For this paper, the two ends of
	a separate, 188 cm long 1-D outer
	loop region were ``attached" to the inlet and outlet of active core region
	model, shown in Figure *, to form a closed coolant loop. This was achieved
	using \gls{DNP} boundary
	conditions at the inlets and outlets of the core and outer loop geometry,
	determined by the inflow and outflow values of each \gls{DNP} group at
	each time-step for each boundary.
	\gls{DNP} in the outer loop are also governed by the same \gls{DNP}
	equations to allow for flow, production, and decay.

	The velocity profile is a uniform velocity of $1.1275$ ms$^{-1}$ throughout
	the active core and outer loop regions. This value is derived from the
	\gls{MSFR} loop circulation time of 4 s. Moltres also has a heat exchanger
	kernel defined for simulating heat loss through
	a heat exchanger. For this paper, the kernel was placed at the midpoint of
	the outer loop region, with the heat loss value fixed to induce an
	approximately 100 K
	drop in temperature as specified by the \gls{MSFR} design inlet/outlet
	temperature difference.

\begin{figure}[t] 
	\centering
	\includegraphics[width=0.46\textwidth]{./figures/reference}
	\captionsetup{justification=centering}
	\caption{Cross-section of the 2D axisymmetric model used for the
	simulation. Derived from the 2D axisymmetric reference model of the MSFR
	\cite{pettersen_coupled_2016}. The figure is not drawn to scale.}
	\label{fig:reference}
\end{figure}

\subsection{\textbf{Moltres Code}}

	This subsection provides the theoretical background for the coupled
	neutronics/thermal-hydraulics physics implemented in Moltres.

	Moltres is an application code developed in the \gls{MOOSE} framework
	\cite{gaston_moose:_2009}. \gls{MOOSE} application codes solve non-linear
	problems through the discretization of \glspl{PDE} on an adaptive coarse
	meshing scheme provided by LibMesh \cite{kirk_libmesh:_2006} and PetSc
	\cite{satish_balay_petsc_2015}. Individual terms of \glspl{PDE} that define
	the physics involved in a system are represented in \gls{MOOSE} (and its
	applications) by kernels. For example, the various terms in the neutron
	diffusion equation such as the diffusion term, time evolution term, etc.
	all have a corresponding physics kernel defined in Moltres. Boundary
	conditions are also handled in a similar fashion. Moltres can solve for an
	arbitrary number of neutronics groups as long as the relevant group
	constants are provided in a Moltres-compatible format.

	As mentioned in the previous Moltres study
	\cite{lindsay_introduction_2018}, the neutronics in Moltres is described by
	the time-independent multi-group neutron diffusion equation as shown in
	Equation \ref{eq1}:
%
\begin{align}
	\frac{1}{v_g} &\frac{\partial \phi_g}{\partial t} - \nabla \cdot D_g \nabla
	\phi_g + \Sigma^r_g \phi_g \nonumber \\ 
	&= \sum^G_{g \neq g'} \Sigma^s_{g' \rightarrow g} \phi_{g'} + \chi^p_g
	\sum^G_{g'=1} (1-\beta) \nu \Sigma^f_{g'} \phi_{g'} + \chi^d_g \sum^I_i
	\lambda_i C_i, \label{eq1}
\end{align}
%
	where

{
\small
\begin{align}
	v_g &= \text{average speed of neutrons in group }g \\
	\phi_g &= \text{flux of neutrons in group }g \\
	t &= \text{time} \\
	D_g &= \text{diffusion coefficient of neutrons in group }g \\
	\Sigma^r_g &= \text{macroscopic cross-section for removal of neutrons} 
	\nonumber \\
	&\text{from group }g \\
	\Sigma^s_{g' \rightarrow g} &= \text{macroscopic cross-section of
	scattering from }g' \text{ to }g \\
	\chi^p_g &= \text{prompt fission spectrum neutrons in group }g \\
	G &= \text{number of discrete neutron groups, }g \\
	\nu &= \text{average number of neutrons produced per fission} \\
	\Sigma^f_{g} &= \text{macroscopic fission cross-section} \nonumber \\
	&\text{for neutron in group }g \\
	\chi^d_g &= \text{delayed fission spectrum neutrons in group }g \\
	I &= \text{number of delayed neutron precursor groups} \\
	\beta &= \text{delayed neutron fraction} \\
	\lambda_i &= \text{average decay constant of delayed neutron} \nonumber \\
	&\text{precursors in precursor group }i \\
	C_i &= \text{concentration of delayed neutron precursors} \nonumber \\
	&\text{in precursor group }i .
\end{align}
}

	The \glspl{DNP} are governed by the following equation:
%
\begin{align}
	\frac{\partial C_i}{\partial t} = \sum^G_{g'=1} \beta_i \nu \Sigma^f_{g'}
	\phi_{g'} - \lambda_i C_i - \frac{\partial}{\partial z} u C_i. \label{eq2}
\end{align}

	Lastly, the governing equation for temperature in the molten salt is given
	as:
%
\begin{align}
	\rho c_{p} \frac{\partial T}{\partial t} + \nabla \cdot \big( \rho
	c_{p} \overrightarrow{u} \cdot T - k \nabla T \big) = Q,
	\label{eq3}
\end{align}
%
	where
{\small
\begin{align}
	\rho &= \text{density of molten salt} \\
	 c_{p} &= \text{specific heat capacity of molten salt} \\
	 T &= \text{temperature of molten salt} \\
	 \overrightarrow{u} &= \text{velocity of molten salt} \\
	 k &= \text{thermal conductivity of molten salt},
\end{align}
	and the source term $Q$ is given as:
%
\begin{align}
Q = \sum^G_{g=1} \epsilon_g \Sigma_g^f \phi_g. \label{eq4}
\end{align}

\section{Steady State Neutron Flux and Temperature Distribution}

	The \gls{MSFR} Moltres simulations were run in transient mode, with
	adaptive time-stepping, and with an
	initial neutron flux of $10^{14}$
	\# cm$^{-2}$ s$^{-1}$ and an initial temperature of 923 K throughout the
	fuel and blanket regions, for the start-up, \gls{BOL}, and equilibrium
	fuel compositions. The simulations reached steady state after 100 s, as the
	volume-integrated neutron flux values varied by less than 0.001\% over the
	last ten seconds. The computational time for each case averages at 30
	minutes when run on four cores on a workstation.

	Figure \ref{fig:totalflux} shows the total radial neutron flux at reactor
	half-height, with the three fuel compositions at steady state. 
	The peak neutron flux value is highest for the start-up composition,
	followed by the \gls{BOL} and equilibrium compositions. All three values
	are slightly lower than the peak value of approximately
	$8.6 \times 10^{15}$ \# cm$^{-2}$ s$^{-1}$ reported by Fiorina et al.
	\cite{fiorina_investigation_2013}. This may be due to the truncation of
	the top and bottom fuel regions of the core for the model used here.
	The vacuum boundary conditions were imposed closer to the center and
	resulted in a lower peak value. Figure \ref{fig:stflux} shows the six
	neutron group fluxes for the start-up fuel composition.

	Heat transfer is dominated by advection as is observed by the temperature
	distributions in Figure \ref{fig:temp}. Given that flux is the highest
	at the center of the core, most of the heat is produced there. The upward
	flow pushes the temperature peak up to the outlet boundary. Tables
	\ref{table:inlet} and \ref{table:outlet} show the average
	fuel inlet and outlet temperatures for the three cases.
%	
\begin{table}[H]
	\centering
	\captionsetup{justification=centering}
	\caption{Average fuel inlet temperature.}
	\begin{tabular}{ll}
		\hline
		{Composition} & {Inlet temperature [K]}\\
		\hline
		Start-up & 964.85\\
		\gls{BOL} & 925.11\\
		Equilibrium & 916.85\\
		\hline
	\end{tabular}
	\label{table:inlet}
\end{table}	
%
\begin{table}[H]
	\centering
	\captionsetup{justification=centering}
	\caption{Average fuel outlet temperature.}
	\begin{tabular}{ll}
		\hline
		{Composition} & {Outlet temperature [K]}\\
		\hline
		Start-up & 1067.40\\
		\gls{BOL} & 1025.39\\
		Equilibrium & 1016.67\\
		\hline
	\end{tabular}
	\label{table:outlet}
\end{table}

	The temperature distribution is very different from the results by Fiorina
	et al. \cite{fiorina_modelling_2014} and Pettersen
	\cite{pettersen_coupled_2016} because we assumed a uniform velocity
	profile. In reality, there is significant flow stagnation in the fuel salt
	near the blanket tank. This causes temperatures to peak near the blanket
	tank as opposed to the center of the core as seen in Figure \ref{fig:temp}.
	However, improved models of the \gls{MSFR}, as shown by Aufiero et al.
	\cite{aufiero_development_2014}, have temperature distributions closer to
	the results in this paper through curved walls that optimize salt flow.

\begin{figure}[H] 
	\centering
	\includegraphics[width=.48\textwidth]{./figures/totalflux}
	\captionsetup{justification=centering}
	\caption{Total radial neutron flux at reactor half-height, for start-up,
	\gls{BOL}, and equilibrium fuel compositions at steady state.}
	\label{fig:totalflux}
\end{figure}

\begin{figure}[H] 
	\centering
	\includegraphics[width=.48\textwidth]{./figures/stflux}
	\captionsetup{justification=centering}
	\caption{Total radial neutron flux at reactor half-height, for start-up,
	\gls{BOL}, and equilibrium fuel compositions at steady state.}
	\label{fig:stflux}
\end{figure}

\begin{figure*}%
\centering
\begin{subfigure}{1\columnwidth}
\includegraphics[width=\columnwidth]{./figures/sttemp}%
\end{subfigure}\hfill%
\begin{subfigure}{1\columnwidth}
\includegraphics[width=\columnwidth]{./figures/eltemp}%
\end{subfigure}\hfill\\
\bigskip
\centering
\begin{subfigure}{1\columnwidth}
\includegraphics[width=\columnwidth]{./figures/eqtemp}%
\label{subfigc}%
\end{subfigure}%
\captionsetup{justification=centering}
\caption{Temperature distributions within the fuel salt region, for start-up
(top left), \gls{BOL} (top right), and equilibrium (bottom) fuel compositions at steady state. The height and radius are in the Y and X directions
respectively.}
\label{fig:temp}
\end{figure*}

\section{Unprotected Loss of Flow}

	An unprotected loss of flow accident may occur due to pump failure. In such
	a scenario, a slower circulation loop is set up through natural convection.
	Previous studies have shown that the pumps coast down
	exponentially with a time constant to a velocity approximately 18 times
	slower \cite{fiorina_modelling_2014}.

\section{Conclusion}

\bibliographystyle{ans}
\bibliography{bibliography}

\end{document}

### 2019-06-16 paper/paper.tex
draft edits

@@
 \end{align}
+}
 	and the source term $Q$ is given as:
@@
 
-	The temperature distribution is very different from the results by Fiorina
-	et al. \cite{fiorina_modelling_2014} and Pettersen
-	\cite{pettersen_coupled_2016} because we assumed a uniform velocity
-	profile. In reality, there is significant flow stagnation in the fuel salt
-	near the blanket tank. This causes temperatures to peak near the blanket
-	tank as opposed to the center of the core as seen in Figure \ref{fig:temp}.
-	However, improved models of the \gls{MSFR}, as shown by Aufiero et al.
-	\cite{aufiero_development_2014}, have temperature distributions closer to
-	the results in this paper through curved walls that optimize salt flow.
-
-\begin{figure}[H] 
-	\centering
-	\includegraphics[width=.48\textwidth]{./figures/totalflux}
-	\captionsetup{justification=centering}
-	\caption{Total radial neutron flux at reactor half-height, for start-up,
-	\gls{BOL}, and equilibrium fuel compositions at steady state.}
-	\label{fig:totalflux}
-\end{figure}
-
-\begin{figure}[H] 
-	\centering
-	\includegraphics[width=.48\textwidth]{./figures/stflux}
-	\captionsetup{justification=centering}
-	\caption{Total radial neutron flux at reactor half-height, for start-up,
-	\gls{BOL}, and equilibrium fuel compositions at steady state.}
-	\label{fig:stflux}
-\end{figure}
-
 \begin{figure*}%
@@
 \end{figure*}
+%
+\begin{figure}[H] 
+	\centering
+	\includegraphics[width=.53\textwidth]{./figures/totalflux}
+	\captionsetup{justification=centering}
+	\caption{Total radial neutron flux at reactor half-height, for start-up,
+	\gls{BOL}, and equilibrium fuel compositions at steady state.}
+	\label{fig:totalflux}
+\end{figure} 
+\begin{figure}[H] 
+	\centering
+	\includegraphics[width=.53\textwidth]{./figures/stflux}
+	\captionsetup{justification=centering}
+	\caption{Neutron group fluxes at reactor half-height, for start-up
+	fuel composition at steady state.}
+	\label{fig:stflux}
+\end{figure}
 
-\section{Unprotected Loss of Flow}
+	The temperature distribution is very different from the results by Fiorina
+	et al. \cite{fiorina_modelling_2014} and Pettersen
+	\cite{pettersen_coupled_2016} because we assumed a uniform velocity
+	profile. In reality, there is significant flow stagnation in the fuel salt
+	near the blanket tank. This causes temperatures to peak near the blanket
+	tank as opposed to the center of the core as seen in Figure \ref{fig:temp}.
+	However, improved models of the \gls{MSFR}, as shown by Aufiero et al.
+	\cite{aufiero_development_2014}, have temperature distributions closer to
+	the results in this paper through curved walls that optimize salt flow.
 
-	An unprotected loss of flow accident may occur due to pump failure. In such
-	a scenario, a slower circulation loop is set up through natural convection.
-	Previous studies have shown that the pumps coast down
-	exponentially with a time constant to a velocity approximately 18 times
-	slower \cite{fiorina_modelling_2014}.
+	Total power as defined by Eq. \ref{eq4} is approximately 2 GW. This
+	is 1 GW less than the rated 3 GW of the \gls{MSFR}. This may be mainly due
+	to the erroneous uniform velocity profile imposed in the core. From
+	fluid dynamics, velocity along the central axis of the core should be
+	higher than the velocity at the periphral areas near the blanket tank.
+	The higher velocity at the center results in higher advective heat transfer
+	away from the center of the core and cools the active region. This should
+	result in an increase in neutron flux from the strongly negative
+	temperature reactivity feedback, and thus higher heat generation. The
+	truncation of the top and bottom fuel salt region is also a factor for
+	the lower than expected heat production.
+
+	Comparing the three different fuel compositions, the \gls{MSFR} operates at
+	the highest temperatures with the start-up fuel composition, followed by
+	the \gls{BOL}, and the equilibrium compositions. This may be due to the
+	generation of $^{233}$Pa as an intermediate for $^{233}$U breeding as
+	mentioned by Rykhlevskii et al. (cite Andrei) in their fuel cycle analysis
+	of the \gls{MSFR}.
+
+\section{Loss of Secondary Cooling Accident}
+
+	A \gls{LOSCA} may occur due to various causes of failure in the secondary
+	coolant loop such as secondary loop pump failure or loss of secondary
+	coolant. While it is less likely in an \gls{MSFR} as it consists of 16
+	separate coolant loops each with its own secondary cooling system, the
+	potential consequences must still be studied.
+	The loss of secondary cooling is simulated by exponentially decreasing
+	the heat loss rate in the Moltres heat exchanger kernel with a time
+	constant of 5 s.
+
+	The loss of heat sink is expected to cause an initial temperature spike,
+	followed by a decrease in neutron flux and heat generation due to the
+	strongly negative temperature reactivity feedback. Eventually, the
+	\gls{MSFR} should settle on a new steady state with a higher average
+	temperature than the operating temperature. If the high temperature is
+	sustained for a long period of time, it could lead to severe damage
+	in the reactor, pipes, or other instruments.
+
+\begin{figure}[b] 
+	\centering
+	\includegraphics[width=.53\textwidth]{./figures/loscatemp}
+	\captionsetup{justification=centering}
+	\caption{Average core fuel temperature for start-up, \gls{BOL}, and
+	equilibrium fuel compositions during \gls{LOSCA}.}
+	\label{fig:loscatemp}
+\end{figure} 
+%
+\begin{figure}[t] 
+	\centering
+	\includegraphics[width=.53\textwidth]{./figures/loscaheat}
+	\captionsetup{justification=centering}
+	\caption{Total thermal power generated, for start-up, \gls{BOL}, and
+	 equilibrium fuel compositions during \gls{LOSCA}.}
+	\label{fig:loscaheat}
+\end{figure}
+
+	As observed in Figure \ref{fig:loscatemp}, the average fuel temperature
+	increased by approximately 10 K and reached the new steady state
+	30-40 s after \gls{LOSCA} began. While the time delay, due to the high
+	initial
+	\gls{DNP} concentration, is in good agreement with results reported by
+	Fiorina et al. \cite{fiorina_modelling_2014}, the temperature rise is much
+	smaller than the 100 K increase reported by the same authors.
+	Power generation fell by two orders of
+	magnitude, resulting in a negligible temperature difference between the
+	inlets and outlets for all three fuel compositions. This could also be
+	attributed to the relatively small total power of 2 GW discussed in the
+	previous section, and the truncated \gls{MSFR} model.
+
+	In comparing the three fuel compositions, a \gls{MSFR} loaded with
+	start-up fuel composition is at a higher risk as it has higher
+	temperatures under normal operating conditions and accident scenarios.
 
 \section{Conclusion}
+
+	Summarise results
+
+	Safe
+
+	Further development of the models is necessary to improve the accuracy
+	and reliability of Moltres as a coupled neutronics/thermal-hydraulics code.
+	Further work includes using an arbitrarily defined velocity profile, such
+	as a parabolic profile. A better option would be to
 

### 2019-06-17 paper/paper.tex

@@
 
-\title{Safety Analysis of the Molten Salt Fast Reactor Fuel Composition using Moltres}
-\author{Sun Myung Park$^{a,b}$, Andrei Rykhlevskii$^a$, and Kathryn D. Huff$^a$}
-\institute{$^a$Dept. of Nuclear, Plasma and Radiological Engineering, University of Illinois at Urbana-Champaign \\
+\title{Safety Analysis of the Molten Salt Fast Reactor Fuel Composition using
+Moltres}
+\author{Sun Myung Park$^{a,b}$, Andrei Rykhlevskii$^a$, and
+Kathryn D. Huff$^a$}
+\institute{$^a$Dept. of Nuclear, Plasma and Radiological Engineering,
+University of Illinois at Urbana-Champaign \\
 $^b$smpark3@illinois.edu}
@@
 %
-    Abstract
+    The Molten
+    Salt Fast Reactor (MSFR) has garnered great interest for its inherent
+    safety and sustainbility features. The MSFR can adopt a closed thorium fuel
+    cycle for
+    sustainable operation through the breeding of $^{233}$U from $^{232}$Th.
+    The fuel composition changes significantly over the course of its lifespan.
+    In this study, we investigated the steady state and transient behavior of
+    the MSFR using Moltres, a coupled neutronics/thermal-hydraulics code
+    developed within the Multiphysics Object Oriented Simulation Environment
+    (MOOSE) framework. Three different fuel compositions, start-up,
+    beginning-of-life (BOL), and equilibrium, were examined for potentially
+    dangerous
+    core temperature excursions during a loss of secondary cooling accident
+    (LOSCA). The steady state peak neutron flux showed good agreement
+    with existing MSFR data, while the temperature distribution and total power
+    showed discrepancies which can be attributed to known sources of error.
+    For the transient behavior under the LOSCA
+    scenario, the time delay towards the new steady state core temperature is
+    also in good agreement with existing MSFR data. Moltres underestimated the
+    temperature rise by a factor of ten relative to other published data, due
+    to the same sources of
+    error for the steady state results. While a MSFR loaded with
+    start-up fuel composition operates at a higher temperature than with the
+    other two fuel compositions, all three cases were shown to be inherently
+    safe due to the strong negative temperature feedback.
 \end{abstract}
@@
     Doppler and density feedback in the fuel salt.  This paper investigates 
-    the impact of changing fuel composition on safety parameters in the 
+    the impact of changing fuel composition on fuel salt temperatures in the 
     \gls{MSFR} concept using a new simulation tool for \glspl{MSR}, Moltres 
@@
     fast-spectrum \gls{MSR} developed under H2020
-    \gls{SAMOFAR} project \cite{serp_molten_2014} (cite gerardin instead).
+    \gls{SAMOFAR} project \cite{gerardin_design_nodate}.
     The \gls{MSFR} boasts several safety and sustainability advantages over
@@
     continuous-energy Monte Carlo code for numerous reactor physics 
-    applications. For verification, we will compare group constants and
-    reactivity coefficients with existing data 
-    \cite{fiorina_analysis_2012,fiorina_investigation_2013} of safety 
-    parameters for the three fuel compositions.  
-    Using these group constants ($\chi$, $\nu\Sigma_f$, 
-    $\Sigma_{g\rightarrow g'}$, $\frac{d\rho}{dT}$, etc.), Moltres then 
+    applications.
+    Using these group constants, Moltres then 
     solves for the flux and temperature based on the neutron diffusion 
-    equation coupled with navier stokes thermal hydraulics. Transient 
-    simulations will establish the spatial distribution of flux, 
-    $\phi_g(\vec{r})$ and temperature, $T(\vec{r})$ during transients.
+    equation coupled with temperature advection due to coolant flow. Transient 
+    simulations will establish core fuel temperatures during transients.
     These distributions will give insight into MSFR transient behavior,
     which will help us identify potential safety risks.
-    These risks may warrant further study and possibly, changes to the
-    fuel composition or the online fuel reprocessing scheme.
 
@@
 	AcF$_4$ represents actinide fluorides such as uranium and thorium
-	fluorides.
-	The \gls{MSFR} supports various fuel compositions. It can run on the same 
+	fluorides. Table \ref{table:fuelsalt} shows the mole fraction of the
+	molecular constituents in the \gls{MSFR} fuel salt.
+	The \gls{MSFR} supports various fuel compositions; it can run on the same 
 	$^{235}$U-$^{238}$U fuel used in most conventional LWRs. It can also run
@@
 	\label{table:msfr}
+\end{table}
+%
+\begin{table}[t]
+\centering
+\begin{tabular}{rr}
+\hline
+{Isotope} & {Mole fraction [\%]}\\
+\hline
+$^7$Li & 29.0\\
+$^{19}$F & 62.6\\
+$^{232}$Th & 7.40\\
+$^{233}$U & 1.00\\
+\hline
+\end{tabular}
+\captionsetup{justification=centering}
+\caption{Fuel salt composition used for the Serpent simulation.}
+\label{table:fuelsalt}
 \end{table}
@@
 	obtained from SCALE/TRITON unit cell depletion calculations by Rykhlevskii
-	et al. (cite Andrei) Their paper used a unit cell model for the modelling
+	et al. \cite{rykhlevskii_fuel_2019} Their paper used a unit cell model for
+	the modelling
 	fuel cycle performance of the \gls{MSFR} and three other fast-spectrum
@@
 	cell SCALE/TRITON models were verified against full core SERPENT models and
-	showed very good agreement. The equilibrium composition was selected at
+	showed very good agreement. We selected the equilibrium composition at
 	approximately 43 years after start-up because the TRU vector change
-	between each depletion time-step from this moment onwards is less than 3\%.
-	(cite Andrei) For the \gls{BOL} composition, it is the fuel composition at
+	between each depletion time-step from this moment onwards is less than 3\%
+	\cite{rykhlevskii_fuel_2019}. For the \gls{BOL} composition, it is the 
+	resulting fuel composition at
 	300 days after start-up. Decay isotopes, whose neutron cross-section data
@@
 
-	Neutronics calculations were performed on SERPENT using these fuel
+	We performed neutronics calculations on SERPENT using these fuel
 	compositions and a truncated, reference \gls{MSFR} core model
@@
 	Moltres.
-	The energy boundaries for the six neutron groups are adopted from previous
+	The energy boundaries for the six neutron groups were adopted from previous
 	\gls{MSFR} studies and shown in Table \ref{table:bound}.
@@
 	initial conditions towards steady state, or from steady state in the case
-	of an accident scenario. The mesh geometry for Moltres is
-	further simplified from the SERPENT model by the omission of the absorber,
+	of an accident scenario. We firther simplified the mesh geometry for
+	Moltres from the SERPENT model by omitting the absorber,
 	heat exchanger, and reflector regions. This is justified as they have
@@
 	inclusion resulted in an extra fine mesh which drastically
-	increased computational time. (Insert Moltres mesh model)
+	increased computational time. Figure \ref{fig:mesh} shows the Moltres
+	\gls{MSFR} mesh.
 
@@
 	loop region were ``attached" to the inlet and outlet of active core region
-	model, shown in Figure *, to form a closed coolant loop. This was achieved
-	using \gls{DNP} boundary
+	model, shown in Figure *, to form a closed coolant loop. We achieved this
+	by using \gls{DNP} boundary
 	conditions at the inlets and outlets of the core and outer loop geometry,
@@
 	each time-step for each boundary.
-	\gls{DNP} in the outer loop are also governed by the same \gls{DNP}
-	equations to allow for flow, production, and decay.
+	The \gls{DNP} equations also govern the \gls{DNP} behavior in the outer
+	loop to allow for flow, production, and decay.
 
@@
 	temperature difference.
-
-\begin{figure}[t] 
-	\centering
-	\includegraphics[width=0.46\textwidth]{./figures/reference}
-	\captionsetup{justification=centering}
-	\caption{Cross-section of the 2D axisymmetric model used for the
-	simulation. Derived from the 2D axisymmetric reference model of the MSFR
-	\cite{pettersen_coupled_2016}. The figure is not drawn to scale.}
-	\label{fig:reference}
-\end{figure}
 
@@
 
+\begin{figure}[t] 
+	\centering
+	\includegraphics[width=0.47\textwidth]{./figures/reference}
+	\captionsetup{justification=centering}
+	\caption{Cross-section of the 2D axisymmetric model used in SERPENT.
+	Derived from the 2D axisymmetric reference model of the MSFR
+	\cite{pettersen_coupled_2016}. Figure is not drawn to scale.}
+	\label{fig:reference}
+\end{figure} 
+%
+\begin{figure}[t] 
+	\centering
+	\includegraphics[width=0.45\textwidth]{./figures/mesh}
+	\captionsetup{justification=centering}
+	\caption{Mesh of the 2D axisymmetric model used in Moltres.
+	The grey and red regions represent the fuel and blanket salt respectively.}
+	\label{fig:mesh}
+\end{figure}
+
 \section{Steady State Neutron Flux and Temperature Distribution}
@@
 \caption{Temperature distributions within the fuel salt region, for start-up
-(top left), \gls{BOL} (top right), and equilibrium (bottom) fuel compositions at steady state. The height and radius are in the Y and X directions
+(top left), \gls{BOL} (top right), and equilibrium (bottom) fuel compositions
+at steady state. The height and radius are in the Y and X directions
 respectively.}
@@
 	away from the center of the core and cools the active region. This should
-	result in an increase in neutron flux from the strongly negative
+	result in an increase in neutron flux from the strong negative
 	temperature reactivity feedback, and thus higher heat generation. The
@@
 	generation of $^{233}$Pa as an intermediate for $^{233}$U breeding as
-	mentioned by Rykhlevskii et al. (cite Andrei) in their fuel cycle analysis
-	of the \gls{MSFR}.
+	mentioned by Rykhlevskii et al. \cite{rykhlevskii_fuel_2019} in their fuel cycle analysis
+	of the \gls{MSFR}; $^{233}$Pa is a significant neutron poison.
 
@@
 	followed by a decrease in neutron flux and heat generation due to the
-	strongly negative temperature reactivity feedback. Eventually, the
+	strong negative temperature reactivity feedback. Eventually, the
 	\gls{MSFR} should settle on a new steady state with a higher average
@@
 
-	Summarise results
+	In this study, we investigated the steady state, and transient behavior of
+	the \gls{MSFR} during a \gls{LOSCA}
+	using the coupled neutronics/thermal-hydraulics code Moltres. Moltres
+	boasts relatively fast computational times due to a combination of
+	parallelization,
+	adaptive coarse meshing scheme and adaptive time-stepping. The total
+	neutron flux at steady state agrees very closely with published results by
+	Fiorina et al. \cite{fiorina_modelling_2014} While the temperature
+	distribution and total power have
+	large discrepancies, we have accounted for the main sources of error:
+	the erroneous uniform velocity profile and the reactor model truncation. We
+	also observed that the \gls{MSFR} operates at a higher temperature with the
+	start-up fuel composition than with the \gls{BOL} and equilibrium
+	compositions, due to the presence of $^{233}$Pa.
 
-	Safe
+	During a \gls{LOSCA}, the \gls{MSFR} core fuel salt temperatures rise by
+	approximately 10 K after a time delay of 30-40 s. While the time delay is
+	similar to published results, the temperature rise is relatively low
+	compared to the 100 K rise reported by Fiorina et al.
+	\cite{fiorina_modelling_2014} This discrepancy is also attributed to the
+	same sources of error for the steady state results. Nonetheless, a
+	temperature rise of
+	this magnitude is relatively benign to reactor components, and makes
+	a strong safety case for \glspl{MSR} due to their strong negative
+	temperature feedback.
 
@@
 	Further work includes using an arbitrarily defined velocity profile, such
-	as a parabolic profile. A better option would be to
+	as a parabolic profile. A better option would be the development of a
+	Navier-Stokes module to generate an accurate velocity profile.
+
+	The heat exchanger functionality in Moltres can also be improved beyond
+	the current implementation of a fixed heat sink. The relevant heat
+	transfer parameters between the primary and secondary loop in the heat
+	exchanger would be necessary for a more complicated heat exchanger system.
 

### 2019-06-17 data/flux-plotter.py
Full paper second draft

@@ -40,7 +40,7 @@ fig, ax = plt.subplots()
 #ax.set_xscale('log')
 #ax.set_yscale('log')
 ax.plot(x[:1000], f[:1000], label=r'Start-up')
-ax.plot(x[:1000], fl[:1000], label=r'Beginning-of-life')
+ax.plot(x[:1000], fl[:1000], label=r'Early-life')
 ax.plot(x[:1000], fq[:1000], label=r'Equilibrium')
 #ax.plot(ts[1:], gs1[1:], label=r'Step')
 ax.set_xlabel(r'Radius [cm]')
@@ -52,7 +52,7 @@ fig, ax = plt.subplots()
 #ax.set_xscale('log')
 #ax.set_yscale('log')
 ax.plot(x[:1000], temp[:1000], label=r'Start-up')
-ax.plot(x[:1000], templ[:1000], label=r'Beginning-of-life')
+ax.plot(x[:1000], templ[:1000], label=r'Early-life')
 ax.plot(x[:1000], tempq[:1000], label=r'Equilibrium')
 #ax.plot(ts[1:], gs1[1:], label=r'Step')
 ax.set_xlabel(r'Radius [cm]')
@@ -78,7 +78,7 @@ fig, ax = plt.subplots()
 #ax.set_xscale('log')
 #ax.set_yscale('log')
 ax.plot(x[:1000], g6[:1000], label=r'Start-up')
-ax.plot(x[:1000], g6l[:1000], label=r'Beginning-of-life')
+ax.plot(x[:1000], g6l[:1000], label=r'Early-life')
 ax.plot(x[:1000], g6q[:1000], label=r'Equilibrium')
 #ax.plot(ts[1:], gs1[1:], label=r'Step')
 ax.set_xlabel(r'Radius [cm]')

### 2019-06-17 data/losca-plotter.py

@@ -40,7 +40,7 @@ fig, ax = plt.subplots()
 ax.set_xscale('log')
 #ax.set_yscale('log')
 ax.plot(t[1:], g1[1:], label=r'Start-up')
-ax.plot(tl[1:], g1l[1:], label=r'Beginning of life')
+ax.plot(tl[1:], g1l[1:], label=r'Early-life')
 ax.plot(tq[1:], g1q[1:], label=r'Equilibrium')
 #ax.plot(ts[1:], gs1[1:], label=r'Step')
 ax.set_xlabel(r'Time [s]')
@@ -51,7 +51,7 @@ fig, ax = plt.subplots()
 #ax.set_xscale('log')
 #ax.set_yscale('log')
 ax.plot(t[1:], temp[1:], label=r'Start-up')
-ax.plot(tl[1:], templ[1:], label=r'Beginning of life')
+ax.plot(tl[1:], templ[1:], label=r'Early-life')
 ax.plot(tq[1:], tempq[1:], label=r'Equilibrium')
 #ax.plot(te[1:], maxe[1:])
 #ax.plot(ts[1:], temps[1:], label=r'Step')
@@ -62,7 +62,7 @@ plt.savefig('loscatemp.png', dpi=400)
 
 fig, ax = plt.subplots()
 ax.plot(t[1:], heat[1:], label=r'Start-up')
-ax.plot(tl[1:], heatl[1:], label=r'Beginning of life')
+ax.plot(tl[1:], heatl[1:], label=r'Early-life')
 ax.plot(tq[1:], heatq[1:], label=r'Equilibrium')
 #ax.plot(ts[1:], heats[1:], label=r'Step')
 ax.set_xlabel(r'Time [s]')

### 2019-06-17 paper/paper.tex

@@
 
-\title{Safety Analysis of the Molten Salt Fast Reactor Fuel Composition using
-Moltres}
+\title{SAFETY ANALYSIS OF THE MOLTEN SALT FAST REACTOR FUEL COMPOSITION USING
+MOLTRES \\~\\~\\~\\}
 \author{Sun Myung Park$^{a,b}$, Andrei Rykhlevskii$^a$, and
@@
 \newcolumntype{a}{>{\hsize=.45\hsize}X}
-\usepackage{titlesec}
-\titleformat*{\subsection}{\normalfont}
-\usepackage[super]{cite}
+%\usepackage{titlesec}
+%\titleformat*{\subsection}{\normalfont}
+%\usepackage[super]{cite}
 \usepackage{multirow}
@@
 %
+\textit{
     The Molten
-    Salt Fast Reactor (MSFR) has garnered great interest for its inherent
+    Salt Fast Reactor (MSFR) has garnered much interest for its inherent
     safety and sustainbility features. The MSFR can adopt a closed thorium fuel
@@
     (MOOSE) framework. Three different fuel compositions, start-up,
-    beginning-of-life (BOL), and equilibrium, were examined for potentially
+    early-life, and equilibrium, were examined for potentially
     dangerous
-    core temperature excursions during a loss of secondary cooling accident
-    (LOSCA). The steady state peak neutron flux showed good agreement
+    core temperature excursions during a unprotected loss of heat sink (ULOHS)
+    accident. The steady state peak neutron flux showed good agreement
     with existing MSFR data, while the temperature distribution and total power
     showed discrepancies which can be attributed to known sources of error.
-    For the transient behavior under the LOSCA
-    scenario, the time delay towards the new steady state core temperature is
-    also in good agreement with existing MSFR data. Moltres underestimated the
-    temperature rise by a factor of ten relative to other published data, due
-    to the same sources of
-    error for the steady state results. While a MSFR loaded with
+    For the transient behavior under the ULOHS
+    scenario, while the transition time towards the new steady state core
+    temperature is also in good agreement with existing MSFR simulations by
+    Fiorina et al., Moltres underestimated the
+    temperature rise by a factor of ten, due to the same sources of
+    error for the steady state results. While an MSFR loaded with
     start-up fuel composition operates at a higher temperature than with the
@@
     safe due to the strong negative temperature feedback.
+}
 \end{abstract}
@@
 	They potentially possess the ability to run for extended 
-    periods with minimal shutdown time due to online fuel reprocessing, which
-    is a clear advantage over solid-fuelled reactors that require significant
-    downtime for refuelling.
-    Their proposed equilibrium fuel compositions differ substantially from
-    start-up compositions due to burnup of initial fissile material and 
-    breeding of new fissile material, but also fissile material feeds and 
-    removal of fission products. Also, while \gls{BOL} fuel composition is
+    periods with minimal shutdown time due to online fuel reprocessing.
+    Their equilibrium fuel compositions differ substantially from
+    start-up compositions not only due to burnup of initial fissile material
+    and breeding of new fissile material, but also fissile material feeds and 
+    removal of fission products. Also, while early-life fuel composition is
     largely dependent on the initial core loading, the long-term equilibrium
@@
     \gls{DNP} governing equations.  The temperature and \gls{DNP} equations
-    fully 
-    account for fuel advection as the fuel salt flows upwards through the 
-    core.
+    fully account for flow via fuel salt advection.
 
@@
     The fast neutron spectrum improves $^{233}$U breeding from $^{232}$Th, an
-    isotope that is about three times as abundant as uranium.
+    isotope that is approximately three times as abundant as uranium.
     Lastly, the \gls{MSFR} operates at near atmospheric pressure; this reduces
@@
     \gls{MSFR} reference model with three fuel compositions:
-    start-up, \gls{BOL}, and equilibrium. In line with the purpose of the
+    start-up, early-life, and equilibrium. In line with the purpose of the
     \gls{MSFR} as a thorium breeder, the chosen start-up fuel composition
     under study is a eutectic mixture of $^{233}$U and 
-    $^{232}$Th fluorides in a lithium fluoride molten salt 
-    \cite{merle-lucotte_launching_2011}, with
+    $^{232}$Th fluorides in a lithium fluoride molten salt, with
     a Th/$^{233}$U mixture feed. $^{233}$U is extracted from
-    the blanket tank and reinserted into the core.
+    the blanket tank and reinserted into the core
+    \cite{merle-lucotte_launching_2011}.
 
@@
     continuous-energy Monte Carlo code for numerous reactor physics 
-    applications.
+    applications. The group constants relevant for Moltres simulations are
+    the various macroscopic neutron cross sections, neutron diffusion
+    coefficient, average fission energy, average neutron yield, inverse
+    neutron speed, fission spectrum, \gls{DNP} decay constants, and effective
+    delayed neutron fractions.
     Using these group constants, Moltres then 
@@
 
-	The \gls{MSFR} is a reference design for a fast-spectrum molten salt
-	reactor
-	first developed under the \gls{EVOL} project, and continued by the
-	\gls{SAMOFAR} project \cite{serp_molten_2014}.
 	Figure \ref{fig:msfr} shows a schematic view of the \gls{MSFR}. The main
@@
 \end{table}
-%
+
 \begin{table}[t]
 \centering
+\captionsetup{justification=centering}
+\caption{Fuel salt composition used for the Serpent simulation.}
 \begin{tabular}{rr}
@@
 \end{tabular}
-\captionsetup{justification=centering}
-\caption{Fuel salt composition used for the Serpent simulation.}
 \label{table:fuelsalt}
@@
 	into the core. The primary heat exchangers transfer heat from the fuel salt 
-	to an intermediate salt coolant loop. There are other instrumentation along
+	to an intermediate salt coolant loop. There is other instrumentation along
 	the external loops for online reprocessing and gas sparging. The core is
@@
 	used to run steady state and transient simulations of the \gls{MSFR}
-	\cite{pettersen_coupled_2016}. This approach allowed for a 3D model
+	\cite{pettersen_coupled_2016}. As \gls{PARCS} only supports conventional
+	fuel assembly shapes, the authors approximated the 3D axisymmetric
+	cylindrical \gls{MSFR} model with
+	hexagonal fuel assemblies. This approach allowed for a 3D model
 	simulation of the \gls{MSFR} on a coarse mesh, thus improving on the 2D
@@
 	steady state simulations, the transient scenarios studied by Pettersen
-	\cite{pettersen_coupled_2016} include loss of heat sink, pump over-speed,
+	include loss of heat sink, pump over-speed,
 	over-cooling and loss of flow.
+
+	As Moltres was first developed solely for the purpose of simulating
+	\glspl{MSR}, it does not require some of the
+	approximations arising from repurposing older codes.
+	This paper aims to present Moltres simulation results and safety analysis
+	of the \gls{MSFR}, for various fuel compositions through its operational
+	lifetime.
 
@@
 	This section describes the overall modelling approach and the codes used
-	in this paper. First, the \gls{BOL} and equilibrium compositions were
+	in this paper. First, the early-life and equilibrium compositions were
 	obtained from SCALE/TRITON unit cell depletion calculations by Rykhlevskii
@@
 	between each depletion time-step from this moment onwards is less than 3\%
-	\cite{rykhlevskii_fuel_2019}. For the \gls{BOL} composition, it is the 
-	resulting fuel composition at
-	300 days after start-up. Decay isotopes, whose neutron cross-section data
-	are not found in the
-	JEFF-3.1.2 nuclear data library, were omitted.
+	\cite{rykhlevskii_fuel_2019}. For the early-life composition, it is the 
+	resulting fuel composition at 300 days after start-up.
 
@@
 	\cite{pettersen_coupled_2016} to generate six-group neutronics data for
-	Moltres.
+	Moltres. Isotopes in the fuel compositions, whose
+	neutron cross-section data are not found in the
+	JEFF-3.1.2 nuclear data library, were omitted from these calculations
 	The energy boundaries for the six neutron groups were adopted from previous
 	\gls{MSFR} studies and shown in Table \ref{table:bound}.
-	As for the \gls{DNP} groups, there are eight groups as defined by the
-	JEFF-3.1.2 nuclear data library used for neutron cross-section data.
+	As for the \gls{DNP}, there are eight \gls{DNP} groups implicitly defined
+	by the JEFF-3.1.2 nuclear data library.
 	The reactor model is a 2D axisymmetric model as shown in
@@
 	The 2D model is extended into a 3D model in SERPENT by rotating it
-	around the central axis to form concentric cylinders.
+	around the central axis to form concentric cylinders. Table
+	\ref{table:reactivity} shows the overall temperature reactivity feedback
+	coefficients due to the Doppler effect and
+	temperature-driven fuel salt expansion. The coefficients were derived by
+	applying a least squares best fit on the multiplication factors at
+	temperatures from 900 K to 1200 K with 50 K intervals.
 
-\begin{table}[b]
+\begin{table}[t]
 	\centering
@@
 \end{table}
+%
+\begin{table}[t]
+	\centering
+	\captionsetup{justification=centering}
+	\caption{Temperature reactivity feedback coefficients.}
+	\begin{tabular}{rr}
+		\hline
+		{Composition} & {$\alpha_T$ [pcm K$^{-1}$]}\\
+		\hline
+		Start-up & $-7.39 \pm 0.03$\\
+		Early-life & $-7.25 \pm 0.03$\\
+		Equilibrium & $-6.24 \pm 0.03$\\
+		\hline
+	\end{tabular}
+	\label{table:reactivity}
+\end{table}
 
@@
 
-	Moltres has a loop app functionality to account for the flow and decay of
-	\glspl{DNP} outside the active core region. For this paper, the two ends of
-	a separate, 188 cm long 1-D outer
-	loop region were ``attached" to the inlet and outlet of active core region
-	model, shown in Figure *, to form a closed coolant loop. We achieved this
-	by using \gls{DNP} boundary
-	conditions at the inlets and outlets of the core and outer loop geometry,
+	Moltres has a salt loop modeling capability to account for the flow and
+	decay of
+	\glspl{DNP} outside the active core region. Moltres applies \gls{DNP}
+	boundary
+	conditions at the inlets and outlets of the core and outer loop,
 	determined by the inflow and outflow values of each \gls{DNP} group at
@@
 	the active core and outer loop regions. This value is derived from the
-	\gls{MSFR} loop circulation time of 4 s. Moltres also has a heat exchanger
-	kernel defined for simulating heat loss through
-	a heat exchanger. For this paper, the kernel was placed at the midpoint of
+	\gls{MSFR} loop circulation time of 4 s. Moltres also has heat exchanger
+	modeling capabilities, represented in \ref{eq3} by the heat sink term. For
+	this paper, it is implemented at the midpoint of
 	the outer loop region, with the heat loss value fixed to induce an
@@
 
-\subsection{\textbf{Moltres Code}}
+\begin{figure}[h] 
+	\centering
+	\includegraphics[width=0.47\textwidth]{./figures/reference}
+	\captionsetup{justification=centering}
+	\caption{Cross-section of the 2D axisymmetric model used in SERPENT.
+	Derived from the 2D axisymmetric reference model of the MSFR
+	\cite{pettersen_coupled_2016}. Figure is not drawn to scale.}
+	\label{fig:reference}
+\end{figure}
+
+\subsection{Moltres Code}
 
@@
 	where
-
-{
-\small
+{\small
 \begin{align}
@@
 	\nonumber \\
-	&\text{from group }g \\
+	&\text{from group }g
+\end{align}
+%
+\begin{align}
 	\Sigma^s_{g' \rightarrow g} &= \text{macroscopic cross-section of
@@
 	\rho c_{p} \frac{\partial T}{\partial t} + \nabla \cdot \big( \rho
-	c_{p} \overrightarrow{u} \cdot T - k \nabla T \big) = Q,
+	c_{p} \overrightarrow{u} \cdot T - k \nabla T \big) = Q_s - Q_{hx},
 	\label{eq3}
@@
 	\overrightarrow{u} &= \text{velocity of molten salt} \\
-	 k &= \text{thermal conductivity of molten salt},
+	k &= \text{thermal conductivity of molten salt} \\
+	Q_{hx} &= \text{heat sink},
 \end{align}
 }
-	and the source term $Q$ is given as:
+	and the source term $Q_s$ is given as:
 %
 \begin{align}
-Q = \sum^G_{g=1} \epsilon_g \Sigma_g^f \phi_g. \label{eq4}
+Q_s = \sum^G_{g=1} \epsilon_g \Sigma_g^f \phi_g. \label{eq4}
 \end{align}
-
-\begin{figure}[t] 
-	\centering
-	\includegraphics[width=0.47\textwidth]{./figures/reference}
-	\captionsetup{justification=centering}
-	\caption{Cross-section of the 2D axisymmetric model used in SERPENT.
-	Derived from the 2D axisymmetric reference model of the MSFR
-	\cite{pettersen_coupled_2016}. Figure is not drawn to scale.}
-	\label{fig:reference}
-\end{figure} 
 %
-\begin{figure}[t] 
+\begin{figure}[h] 
 	\centering
@@
 
-\section{Steady State Neutron Flux and Temperature Distribution}
+\section{Steady State Neutron Flux \\and Temperature Distribution}
 
@@
 	initial neutron flux of $10^{14}$
-	\# cm$^{-2}$ s$^{-1}$ and an initial temperature of 923 K throughout the
-	fuel and blanket regions, for the start-up, \gls{BOL}, and equilibrium
+	cm$^{-2}$ s$^{-1}$ and an initial temperature of 923 K throughout the
+	fuel and blanket regions, for the start-up, early-life, and equilibrium
 	fuel compositions. The simulations reached steady state after 100 s, as the
@@
 	The peak neutron flux value is highest for the start-up composition,
-	followed by the \gls{BOL} and equilibrium compositions. All three values
+	followed by the early-life and equilibrium compositions. All three values
 	are slightly lower than the peak value of approximately
-	$8.6 \times 10^{15}$ \# cm$^{-2}$ s$^{-1}$ reported by Fiorina et al.
+	$8.6 \times 10^{15}$ cm$^{-2}$ s$^{-1}$ reported by Fiorina et al.
 	\cite{fiorina_investigation_2013}. This may be due to the truncation of
@@
 	fuel inlet and outlet temperatures for the three cases.
-%	
-\begin{table}[H]
+
+\begin{table}[t]
 	\centering
@@
 	\caption{Average fuel inlet temperature.}
-	\begin{tabular}{ll}
+	\begin{tabular}{rr}
 		\hline
@@
 		Start-up & 964.85\\
-		\gls{BOL} & 925.11\\
+		Early-life & 925.11\\
 		Equilibrium & 916.85\\
@@
 %
-\begin{table}[H]
+\begin{table}[t]
 	\centering
@@
 	\caption{Average fuel outlet temperature.}
-	\begin{tabular}{ll}
+	\begin{tabular}{rr}
 		\hline
@@
 		Start-up & 1067.40\\
-		\gls{BOL} & 1025.39\\
+		Early-life & 1025.39\\
 		Equilibrium & 1016.67\\
@@
 \end{table}	
-
+%
+\begin{figure}[b] 
+	\centering
+	\includegraphics[width=.53\textwidth]{./figures/totalflux}
+	\captionsetup{justification=centering}
+	\caption{Total radial neutron flux at reactor half-height, for start-up,
+	early-life, and equilibrium fuel compositions at steady state.}
+	\label{fig:totalflux}
+\end{figure} 
+%
+\begin{figure}[t] 
+	\centering
+	\includegraphics[width=.53\textwidth]{./figures/stflux}
+	\captionsetup{justification=centering}
+	\caption{Neutron group fluxes at reactor half-height, for start-up
+	fuel composition at steady state.}
+	\label{fig:stflux}
+\end{figure} 
+%
 \begin{figure*}%
@@
 \caption{Temperature distributions within the fuel salt region, for start-up
-(top left), \gls{BOL} (top right), and equilibrium (bottom) fuel compositions
+(top left), early-life (top right), and equilibrium (bottom) fuel compositions
 at steady state. The height and radius are in the Y and X directions
@@
 \end{figure*}
-%
-\begin{figure}[H] 
-	\centering
-	\includegraphics[width=.53\textwidth]{./figures/totalflux}
-	\captionsetup{justification=centering}
-	\caption{Total radial neutron flux at reactor half-height, for start-up,
-	\gls{BOL}, and equilibrium fuel compositions at steady state.}
-	\label{fig:totalflux}
-\end{figure} 
-\begin{figure}[H] 
-	\centering
-	\includegraphics[width=.53\textwidth]{./figures/stflux}
-	\captionsetup{justification=centering}
-	\caption{Neutron group fluxes at reactor half-height, for start-up
-	fuel composition at steady state.}
-	\label{fig:stflux}
-\end{figure}
 
-	The temperature distribution is very different from the results by Fiorina
-	et al. \cite{fiorina_modelling_2014} and Pettersen
-	\cite{pettersen_coupled_2016} because we assumed a uniform velocity
-	profile. In reality, there is significant flow stagnation in the fuel salt
-	near the blanket tank. This causes temperatures to peak near the blanket
+	The average outlet temperatures for all three compositions are close to
+	the \gls{MSFR} outlet temperature specification of 1023 K. Due to having a
+	Reynolds number, significant
+	mixing and heat transfer is expected in the fuel salt as it flows
+	out of the core and through the outer loop. However, the center of the top
+	reflector region is exposed to dangerously high peak temperatures
+	of greater than 1100 K in all three cases as observed in Figure
+	\ref{fig:temp}. In addition, higher temperatures
+	are expected during dangerous accident scenarios.
+
+	In actuality, the peak temperatures are likely to be lower than the values
+	seen in Figure \ref{fig:temp} because of turbulent mixing. In choosing a
+	uniform velocity profile, we have also implied that flow is laminar, which
+	is a weak assumption given the high Reynolds number of molten salt flow in
+	the \gls{MSFR}. Turbulent temperature mixing could potentially be
+	approximated by
+	incorporating it into the conduction term as turbulent diffusion.
+
+	The uniform velocity approximation in our models also resulted in a
+	significantly different spatial temperature distribution shape as compared
+	to
+	the results by Fiorina et al. \cite{fiorina_modelling_2014} and Pettersen
+	\cite{pettersen_coupled_2016}. Their models feature significant flow
+	stagnation in the fuel salt
+	near the blanket tank. This causes their temperatures distributions to peak
+	near the blanket
 	tank as opposed to the center of the core as seen in Figure \ref{fig:temp}.
@@
 	the highest temperatures with the start-up fuel composition, followed by
-	the \gls{BOL}, and the equilibrium compositions. This may be due to the
+	the early-life, and the equilibrium compositions. This may be due to the
 	generation of $^{233}$Pa as an intermediate for $^{233}$U breeding as
-	mentioned by Rykhlevskii et al. \cite{rykhlevskii_fuel_2019} in their fuel cycle analysis
+	mentioned by Rykhlevskii et al. \cite{rykhlevskii_fuel_2019} in their fuel
+	cycle analysis
 	of the \gls{MSFR}; $^{233}$Pa is a significant neutron poison.
 
-\section{Loss of Secondary Cooling Accident}
+\section{Unprotected Loss of Heat Sink}
 
-	A \gls{LOSCA} may occur due to various causes of failure in the secondary
+	\gls{ULOHS} may occur due to various causes of failure in the heat
+	exchanger or secondary
 	coolant loop such as secondary loop pump failure or loss of secondary
@@
 
-	The loss of heat sink is expected to cause an initial temperature spike,
+	\gls{ULOHS} is expected to cause temperatures to increase,
 	followed by a decrease in neutron flux and heat generation due to the
@@
 
-\begin{figure}[b] 
+\begin{figure}[t] 
 	\centering
@@
 	\captionsetup{justification=centering}
-	\caption{Average core fuel temperature for start-up, \gls{BOL}, and
-	equilibrium fuel compositions during \gls{LOSCA}.}
+	\caption{Average core fuel temperature for start-up, early-life, and
+	equilibrium fuel compositions during \gls{ULOHS}.}
 	\label{fig:loscatemp}
@@
 	\captionsetup{justification=centering}
-	\caption{Total thermal power generated, for start-up, \gls{BOL}, and
-	 equilibrium fuel compositions during \gls{LOSCA}.}
+	\caption{Total thermal power generated, for start-up, early-life, and
+	 equilibrium fuel compositions during \gls{ULOHS}.}
 	\label{fig:loscaheat}
@@
 	As observed in Figure \ref{fig:loscatemp}, the average fuel temperature
-	increased by approximately 10 K and reached the new steady state
-	30-40 s after \gls{LOSCA} began. While the time delay, due to the high
-	initial
-	\gls{DNP} concentration, is in good agreement with results reported by
+	starts rising approximately 0.7 s after initiation. The \gls{MSFR} reaches
+	a new steady state approximately 10 K higher than the initial temperature
+	after 30 s. While the transition time to reach the new steady state is in
+	good agreement with results reported by
 	Fiorina et al. \cite{fiorina_modelling_2014}, the temperature rise is much
 	smaller than the 100 K increase reported by the same authors.
-	Power generation fell by two orders of
+	Power generation falls by two orders of
 	magnitude, resulting in a negligible temperature difference between the
@@
 
-	In comparing the three fuel compositions, a \gls{MSFR} loaded with
-	start-up fuel composition is at a higher risk as it has higher
+	In comparing the three fuel compositions, an \gls{MSFR} loaded with
+	start-up fuel composition is at a higher safety risk as it has higher
 	temperatures under normal operating conditions and accident scenarios.
@@
 	In this study, we investigated the steady state, and transient behavior of
-	the \gls{MSFR} during a \gls{LOSCA}
+	the \gls{MSFR} during a \gls{ULOHS}
 	using the coupled neutronics/thermal-hydraulics code Moltres. Moltres
@@
 	neutron flux at steady state agrees very closely with published results by
-	Fiorina et al. \cite{fiorina_modelling_2014} While the temperature
+	Fiorina et al. \cite{fiorina_modelling_2014}.
+
+	While the temperature
 	distribution and total power have
@@
 	also observed that the \gls{MSFR} operates at a higher temperature with the
-	start-up fuel composition than with the \gls{BOL} and equilibrium
-	compositions, due to the presence of $^{233}$Pa.
+	start-up fuel composition than with the early-life and equilibrium
+	compositions, due to the presence of $^{233}$Pa. The high peak temperatures 
+	near the center of the top reflector are a potential safety risk. While
+	this high temperatures could have been exacerbated by absence of turbulent
+	diffusion implementation in Moltres, it warrants the need for further
+	safety analysis.
 
-	During a \gls{LOSCA}, the \gls{MSFR} core fuel salt temperatures rise by
-	approximately 10 K after a time delay of 30-40 s. While the time delay is
+	During a \gls{ULOHS}, the \gls{MSFR} core fuel salt temperatures rise by
+	approximately 10 K after a transition time of 30 s. While this time
+	duration is
 	similar to published results, the temperature rise is relatively low
@@
 	a strong safety case for \glspl{MSR} due to their strong negative
-	temperature feedback.
+	temperature feedback, with the exception of the central top reflector
+	region discussed previously.
 
@@
 	as a parabolic profile. A better option would be the development of a
-	Navier-Stokes module to generate an accurate velocity profile.
+	Navier-Stokes module to generate an accurate velocity profile. A turbulent
+	diffusion model would also be an essential addition to account for
+	turbulent temperature mixing.
 
-	The heat exchanger functionality in Moltres can also be improved beyond
+	The heat exchanger functionality in Moltres can be improved beyond
 	the current implementation of a fixed heat sink. The relevant heat
@@
 
+%\begin{center}
+%\section*{Acknowledgements}
+%\end{center}
+
+%Acknowledgements \\
+
+\begin{center}
 	\bibliographystyle{ans}
 	\bibliography{bibliography}
+\end{center}
 

### 2019-08-01 paper/paper.tex
Review edits

@@
 \institute{$^a$Dept. of Nuclear, Plasma and Radiological Engineering,
-University of Illinois at Urbana-Champaign \\
-$^b$smpark3@illinois.edu}
+University of Illinois at Urbana-Champaign}
+\email{$^b$smpark3@illinois.edu}
 
 \usepackage{graphicx} % allows inclusion of graphics
-\usepackage{booktabs} % nice rules (thick lines) for tables
+%\usepackage{booktabs} % nice rules (thick lines) for tables
 \usepackage{microtype} % improves typography for PDF
@@
 \usepackage[labelfont=bf]{caption}
-%\captionsetup[table]{name=Table}
-\renewcommand{\thetable}{\arabic{table}}
 \usepackage{caption}
@@
 \usepackage{siunitx}
-\newcolumntype{c}{>{\hsize=.56\hsize}X}
-\newcolumntype{b}{>{\hsize=.7\hsize}X}
+%\newcolumntype{c}{>{\hsize=.56\hsize}X}
+%\newcolumntype{b}{>{\hsize=.7\hsize}X}
 %\newcolumntype{s}{>{\hsize=.74\hsize}X}
-\newcolumntype{f}{>{\hsize=.1\hsize}X}
-\newcolumntype{a}{>{\hsize=.45\hsize}X}
+%\newcolumntype{f}{>{\hsize=.1\hsize}X}
+%\newcolumntype{a}{>{\hsize=.45\hsize}X}
 %\usepackage{titlesec}
@@
 \usepackage{hhline}
+\usepackage{dcolumn}
 
@@
     core temperature excursions during a unprotected loss of heat sink (ULOHS)
-    accident. The steady state peak neutron flux showed good agreement
-    with existing MSFR data, while the temperature distribution and total power
+    accident. The six-group and total neutron flux distributions 
+    showed good agreement with SERPENT and
+    published MSFR results, while the temperature distribution and total power
     showed discrepancies which can be attributed to known sources of error.
@@
     temperature rise by a factor of ten, due to the same sources of
-    error for the steady state results. While an MSFR loaded with
+    error affecting the steady state results. While an MSFR loaded with
     start-up fuel composition operates at a higher temperature than with the
@@
     simulations will establish core fuel temperatures during transients.
-    These distributions will give insight into MSFR transient behavior,
+    These distributions will give insight into \gls{MSFR} transient behavior,
     which will help us identify potential safety risks.
 
-\section{Molten Salt Fast Reactor}
-
-	Figure \ref{fig:msfr} shows a schematic view of the \gls{MSFR}. The main
-	specifications of the \gls{MSFR} are given in Table \ref{table:msfr}.
-
-	Lithium fluoride (LiF) is the major component of the fuel and blanket
-	molten salts used for the \gls{MSFR}. Fissile and fertile isotopes are
-	introduced
-	into the mixture by mole fractions of 77.5\%LiF-22.5\%AcF$_4$, where
-	AcF$_4$ represents actinide fluorides such as uranium and thorium
-	fluorides. Table \ref{table:fuelsalt} shows the mole fraction of the
-	molecular constituents in the \gls{MSFR} fuel salt.
-	The \gls{MSFR} supports various fuel compositions; it can run on the same 
-	$^{235}$U-$^{238}$U fuel used in most conventional LWRs. It can also run
-	on a
-	mixture of fresh and used uranium fuel containing reprocessed TRU
-	isotopes \cite{fiorina_investigation_2013}. However, the main configuration
-	of the \gls{MSFR} is a breeder reactor running on $^{233}$U-$^{232}$Th
-	\cite{merle-lucotte_launching_2011}. Previous studies have reported
-	breeding ratios of up to 1.1 on the \gls{MSFR} \cite{fiorina_molten_2013}.
-
-\begin{figure}[t] 
+\begin{figure}[h] 
 	\centering
@@
 
-\begin{table}[t]
+\begin{table}[h]
 	\caption{Specifications of the \gls{MSFR} design \cite{serp_molten_2014}.}
@@
 \caption{Fuel salt composition used for the Serpent simulation.}
-\begin{tabular}{rr}
+\begin{tabular}{lS}
 \hline
@@
 \label{table:fuelsalt}
+\vspace{.5cm}
+	\centering
+	\captionsetup{justification=centering}
+	\caption{Fuel and blanket salt properties. $T$ denotes temperature in
+	Kelvins.}
+	{\small
+	\begin{tabular}{ll}
+		\hline
+		{Property} & {Value}\\
+		\hline
+		Density, $\rho$ [kg m$^{-3}$] & $4983.56 - 0.882 \cdot T$ \\
+		Thermal cond. , $k$ [W m$^{-1}$ K$^{-1}$] & $0.928 + 8.397 \times 10
+		^{-5} \cdot T$\\
+		Specific heat, $c_p$ [J kg$^{-1}$ K$^{-1}$] & $-1111 + 2.78 \cdot T$ \\
+		\hline
+	\end{tabular}
+	}
+	\vspace{.5cm}
+	\label{table:saltprop}
+	\centering
+	\captionsetup{justification=centering}
+	\caption{Material compositions and densities of the absorber,
+	and reflector regions. All elements listed are in their natural
+	compositions.}
+	{\small
+	\begin{tabular}{llSr}
+		\hline
+		Region & Element & At\% & Density [kg m$^{-3}$]\\
+		\hline
+		\multirow{2}{*}{Absorber} & B & 80  & \multirow{2}{*}{2520}\\
+		& C & 20 & \\
+		\hline
+		\multirow{4}{*}{Reflector} & Ni & 67.7 & \multirow{4}{*}{10000} \\
+		& W & 25.0 & \\
+		& Cr & 7.0 & \\
+		& Al & 0.3 & \\
+		\hline
+	\end{tabular}
+	}
+	\label{table:material}
 \end{table}
+
+    Section II provides the specifications and a literature review of the
+    \gls{MSFR} concept. Section III covers the overall modeling approach with
+    respect to the codes used in this study: SERPENT and Moltres. Section IV
+    presents steady state neutron flux and temperature distribution results
+    from Moltres for the three different fuel compositions studied. Section V
+    explores the \gls{MSFR}'s neutronic and thermodynamic response to a
+    \gls{ULOHS} scenario. Lastly, Section VI provides conclusions and
+    suggestions for future work.
+
+\section{Molten Salt Fast Reactor}
+
+	Figure \ref{fig:msfr} shows a schematic view of the \gls{MSFR}. The main
+	specifications of the \gls{MSFR} are given in Table \ref{table:msfr}.
+
+	Lithium fluoride (LiF) is the major component of the fuel and blanket
+	molten salts used for the \gls{MSFR}. Fissile and fertile isotopes are
+	introduced
+	into the mixture by mole fractions of 77.5\%LiF-22.5\%AcF$_4$, where
+	AcF$_4$ represents actinide fluorides such as uranium and thorium
+	fluorides. Table \ref{table:fuelsalt} shows the mole fraction of the
+	molecular constituents in the \gls{MSFR} fuel salt, with the relevant
+	physical properties in Table \ref{table:saltprop}.
+	The \gls{MSFR} supports various fuel compositions; it can run on the same 
+	$^{235}$U-$^{238}$U fuel used in most conventional LWRs. It can also run
+	on a
+	mixture of fresh and used uranium fuel containing reprocessed TRU
+	isotopes \cite{fiorina_investigation_2013}. However, the main configuration
+	of the \gls{MSFR} is a breeder reactor running on $^{233}$U-$^{232}$Th
+	\cite{merle-lucotte_launching_2011}. Previous studies have reported
+	breeding ratios of up to 1.1 on the \gls{MSFR} \cite{fiorina_molten_2013}.
 
@@
 	multiphysics simulations for the \gls{MSFR}. A paper by Fiorina et al.
-	\cite{fiorina_modelling_2014} compares results between coupled models
-	developed on the multiphysics code COMSOL and an in-house code developed at
+	\cite{fiorina_modelling_2014} compares results between models
+	developed on the multiphysics software COMSOL, and coupled in-house codes
+	developed at
 	Delft University of Technology. The models used 2D axisymmetric models of
@@
 	hexagonal fuel assemblies. This approach allowed for a 3D model
-	simulation of the \gls{MSFR} on a coarse mesh, thus improving on the 2D
-	axisymmetric COMSOL/TUDelft models with the benefit of much lower
-	computation times in comparison to the CFD-OpenFOAM models. On top of
+	simulation of the \gls{MSFR} on a coarse mesh and showed good agreement
+	with the COMSOL and TUDelft models with the benefit of much lower
+	computation times in comparison to the OpenFOAM CFD model. On top of
 	steady state simulations, the transient scenarios studied by Pettersen
-	include loss of heat sink, pump over-speed,
-	over-cooling and loss of flow.
+	include loss of heat sink, pump over-speed, over-cooling and loss of flow.
 
-	As Moltres was first developed solely for the purpose of simulating
-	\glspl{MSR}, it does not require some of the
-	approximations arising from repurposing older codes.
+	As Moltres is developed on the \gls{MOOSE} framework, it can perform
+	implicit multiphysics coupling on an adaptive meshing scheme over multiple
+	processing units for accurate and efficient \gls{MSR} simulations.
 	This paper aims to present Moltres simulation results and safety analysis
@@
 	obtained from SCALE/TRITON unit cell depletion calculations by Rykhlevskii
-	et al. \cite{rykhlevskii_fuel_2019} Their paper used a unit cell model for
-	the modelling
+	et al. \cite{rykhlevskii_fuel_2019} The authors used unit cell
+	approximations for the modeling
 	fuel cycle performance of the \gls{MSFR} and three other fast-spectrum
-	\glspl{MSR}. The neutron spectrum and depletion calculations on the unit
-	cell SCALE/TRITON models were verified against full core SERPENT models and
-	showed very good agreement. We selected the equilibrium composition at
+	\glspl{MSR}. We selected the equilibrium composition at
 	approximately 43 years after start-up because the TRU vector change
@@
 	\cite{pettersen_coupled_2016} to generate six-group neutronics data for
-	Moltres. Isotopes in the fuel compositions, whose
+	Moltres. The material compositions and densities for the absorber,
+	and reflector regions are given in Table \ref{table:material}. We set a
+	neutron population of 200,000 with 50 inactive cycles and 500 active
+	cycles. For
+	simplicity, the heat exchanger and pump region were modeled after
+	Hastelloy N \cite{hastelloy_2017}. Isotopes in the fuel compositions, whose
 	neutron cross-section data are not found in the
@@
 	\caption{Neutron energy group upper bounds used in Serpent.}
-	\begin{tabular}{ll}
+	\begin{tabular}{c S}
 		\hline
@@
 	\label{table:bound}
-\end{table}
-%
-\begin{table}[t]
 	\centering
@@
 	\caption{Temperature reactivity feedback coefficients.}
-	\begin{tabular}{rr}
+	\begin{tabular}{lr}
 		\hline
@@
 \end{table}	
-
+%	
 	Finally, with the group constant data from SERPENT, Moltres
@@
 
-\begin{figure}[h] 
+\begin{figure}[t] 
 	\centering
@@
 	\caption{Cross-section of the 2D axisymmetric model used in SERPENT.
-	Derived from the 2D axisymmetric reference model of the MSFR
-	\cite{pettersen_coupled_2016}. Figure is not drawn to scale.}
+	Derived from the \gls{MSFR} reference model
+	\cite{pettersen_coupled_2016}. Figure is not drawn to scale. All dimensions
+	are in cm.}
 	\label{fig:reference}
@@
 	arbitrary number of neutronics groups as long as the relevant group
-	constants are provided in a Moltres-compatible format.
+	constants are provided in a compatible text format.
 
@@
 {\small
-\begin{align}
+\begin{align*}
 	v_g &= \text{average speed of neutrons in group }g \\
@@
 	&\text{from group }g
-\end{align}
+\end{align*}
 %
-\begin{align}
+\begin{align*}
 	\Sigma^s_{g' \rightarrow g} &= \text{macroscopic cross-section of
@@
 	&\text{in precursor group }i .
-\end{align}
+\end{align*}
 }
@@
 {\small
-\begin{align}
+\begin{align*}
 	\rho &= \text{density of molten salt} \\
@@
 	Q_{hx} &= \text{heat sink},
-\end{align}
+\end{align*}
 }
@@
 
-	The \gls{MSFR} Moltres simulations were run in transient mode, with
-	adaptive time-stepping, and with an
-	initial neutron flux of $10^{14}$
+	We first ran Moltres in steady-state solver mode to generate the six-group
+	neutron flux distribution at a temperature of 973 K with the start-up fuel
+	composition. This
+	is verified against the six-group flux generated directly from SERPENT
+	after collapsing the fine-group flux.
+	Figure \ref{fig:ntflux} shows the neutron flux
+	distributions from SERPENT and Moltres, with precursor drift disabled for
+	code verification. There is very good agreement between the six group
+	flux distributions from SERPENT and Moltres.
+
+	Next, the \gls{MSFR} Moltres simulations were
+	run in transient mode, with adaptive time-stepping and an
+	initial, uniform neutron flux of $10^{14}$
 	cm$^{-2}$ s$^{-1}$ and an initial temperature of 923 K throughout the
@@
 	volume-integrated neutron flux values varied by less than 0.001\% over the
-	last ten seconds. The computational time for each case averages at 30
-	minutes when run on four cores on a workstation.
+	previous ten seconds. The computational time for each case averages at 30
+	minutes when run on four processing units on a workstation.
 
-	Figure \ref{fig:totalflux} shows the total radial neutron flux at reactor
-	half-height, with the three fuel compositions at steady state. 
-	The peak neutron flux value is highest for the start-up composition,
-	followed by the early-life and equilibrium compositions. All three values
-	are slightly lower than the peak value of approximately
-	$8.6 \times 10^{15}$ cm$^{-2}$ s$^{-1}$ reported by Fiorina et al.
-	\cite{fiorina_investigation_2013}. This may be due to the truncation of
-	the top and bottom fuel regions of the core for the model used here.
-	The vacuum boundary conditions were imposed closer to the center and
-	resulted in a lower peak value. Figure \ref{fig:stflux} shows the six
-	neutron group fluxes for the start-up fuel composition.
-
-	Heat transfer is dominated by advection as is observed by the temperature
-	distributions in Figure \ref{fig:temp}. Given that flux is the highest
-	at the center of the core, most of the heat is produced there. The upward
-	flow pushes the temperature peak up to the outlet boundary. Tables
-	\ref{table:inlet} and \ref{table:outlet} show the average
-	fuel inlet and outlet temperatures for the three cases.
-
-\begin{table}[t]
+\begin{table}[b]
 	\centering
@@
 	\caption{Average fuel inlet temperature.}
-	\begin{tabular}{rr}
+	\begin{tabular}{lS}
 		\hline
@@
 	\label{table:inlet}
-\end{table}	
-%
-\begin{table}[t]
 	\centering
@@
 	\caption{Average fuel outlet temperature.}
-	\begin{tabular}{rr}
+	\begin{tabular}{lS}
 		\hline
@@
 %
-\begin{figure}[b] 
+\begin{figure}[htbp] 
 	\centering
-	\includegraphics[width=.53\textwidth]{./figures/totalflux}
+	\includegraphics[width=.48\textwidth]{./figures/nt-spec}
+	\captionsetup{justification=centering}
+	\caption{Fine-group and six-group neutron flux\\ distributions from SERPENT
+	and Moltres.}
+	\label{fig:ntflux}
+	\centering
+	\includegraphics[width=.48\textwidth]{./figures/totalflux}
 	\captionsetup{justification=centering}
@@
 	\label{fig:totalflux}
-\end{figure} 
-%
-\begin{figure}[t] 
 	\centering
-	\includegraphics[width=.53\textwidth]{./figures/stflux}
+	\includegraphics[width=.48\textwidth]{./figures/stflux}
 	\captionsetup{justification=centering}
@@
 %
-\begin{figure*}%
+\begin{figure*}[htbp]%
 \centering
@@
 \end{figure*}
+
+	Figure \ref{fig:totalflux} shows the total radial neutron flux at reactor
+	half-height, with the three fuel compositions at steady state. 
+	The peak neutron flux value is highest for the start-up composition,
+	followed by the early-life and equilibrium compositions. All three values
+	are slightly lower than the peak value of approximately
+	$8.6 \times 10^{15}$ cm$^{-2}$ s$^{-1}$ reported by Fiorina et al.
+	\cite{fiorina_investigation_2013}. This may be due to the truncation of
+	the top and bottom fuel regions of the core for the model used here.
+	The vacuum boundary conditions were imposed closer to the center and
+	resulted in a lower peak value. Figure \ref{fig:stflux} shows the six
+	neutron group fluxes for the start-up fuel composition.
+
+	Heat transfer is dominated by advection as is observed by the temperature
+	distributions in Figure \ref{fig:temp}. Given that flux is the highest
+	at the center of the core, most of the heat is produced there. The upward
+	flow pushes the temperature peak up to the outlet boundary. Tables
+	\ref{table:inlet} and \ref{table:outlet} show the average
+	fuel inlet and outlet temperatures for the three cases.
 
@@
 
-	Total power as defined by Eq. \ref{eq4} is approximately 2 GW. This
+	Total power, as defined by Eq. \ref{eq4}, at steady state is approximately
+	2 GW. This
 	is 1 GW less than the rated 3 GW of the \gls{MSFR}. This may be mainly due
@@
 	cycle analysis
-	of the \gls{MSFR}; $^{233}$Pa is a significant neutron poison.
+	of the \gls{MSFR}; $^{233}$Pa is a precursor for the $^{234}$U neutron
+	poison.
+
+\begin{figure}[t] 
+	\centering
+	\includegraphics[width=.48\textwidth]{./figures/loscatemp}
+	\captionsetup{justification=centering}
+	\caption{Rise in average core fuel temperature for start-up, early-life,
+	and equilibrium fuel compositions during \gls{ULOHS}.}
+	\label{fig:loscatemp}
+	\centering
+	\includegraphics[width=.48\textwidth]{./figures/loscaheat}
+	\captionsetup{justification=centering}
+	\caption{Power generated, for start-up, early-life, and
+	 equilibrium fuel compositions during \gls{ULOHS}.}
+	\label{fig:loscaheat}
+\end{figure}
 
@@
 
-\begin{figure}[t] 
-	\centering
-	\includegraphics[width=.53\textwidth]{./figures/loscatemp}
-	\captionsetup{justification=centering}
-	\caption{Average core fuel temperature for start-up, early-life, and
-	equilibrium fuel compositions during \gls{ULOHS}.}
-	\label{fig:loscatemp}
-\end{figure} 
-%
-\begin{figure}[t] 
-	\centering
-	\includegraphics[width=.53\textwidth]{./figures/loscaheat}
-	\captionsetup{justification=centering}
-	\caption{Total thermal power generated, for start-up, early-life, and
-	 equilibrium fuel compositions during \gls{ULOHS}.}
-	\label{fig:loscaheat}
-\end{figure}
-
 	As observed in Figure \ref{fig:loscatemp}, the average fuel temperature
@@
 	Power generation falls by two orders of
-	magnitude, resulting in a negligible temperature difference between the
+	magnitude (Figure \ref{fig:loscaheat}),
+	resulting in a negligible temperature difference between the
 	inlets and outlets for all three fuel compositions. This could also be
@@
 	boasts relatively fast computational times due to a combination of
-	parallelization,
-	adaptive coarse meshing scheme and adaptive time-stepping. The total
+	parallelization, adaptive coarse meshing scheme and adaptive time-stepping.
+	We verified the six-group neutron flux distribution at 973 K from Moltres
+	against SERPENT. The total peak
 	neutron flux at steady state agrees very closely with published results by

### 2019-08-01 data/losca-plotter.py

@@ -50,23 +50,23 @@ ax.legend()
 fig, ax = plt.subplots()
 #ax.set_xscale('log')
 #ax.set_yscale('log')
-ax.plot(t[1:], temp[1:], label=r'Start-up')
-ax.plot(tl[1:], templ[1:], label=r'Early-life')
-ax.plot(tq[1:], tempq[1:], label=r'Equilibrium')
+ax.plot(t[1:], temp[1:] - temp[1], label=r'Start-up')
+ax.plot(tl[1:], templ[1:] - templ[1], label=r'Early-life')
+ax.plot(tq[1:], tempq[1:] - tempq[1], label=r'Equilibrium')
 #ax.plot(te[1:], maxe[1:])
 #ax.plot(ts[1:], temps[1:], label=r'Step')
 ax.set_xlabel(r'Time [s]')
-ax.set_ylabel(r'Average fuel temperature [K]')
+ax.set_ylabel(r'Rise in average fuel temperature in core [K]')
 ax.legend()
 plt.savefig('loscatemp.png', dpi=400)
 
 fig, ax = plt.subplots()
-ax.plot(t[1:], heat[1:], label=r'Start-up')
-ax.plot(tl[1:], heatl[1:], label=r'Early-life')
-ax.plot(tq[1:], heatq[1:], label=r'Equilibrium')
+ax.plot(t[1:], heat[1:] / max(heat), label=r'Start-up')
+ax.plot(tl[1:], heatl[1:] / max(heatl), label=r'Early-life')
+ax.plot(tq[1:], heatq[1:] / max(heatq), label=r'Equilibrium')
 #ax.plot(ts[1:], heats[1:], label=r'Step')
 ax.set_xlabel(r'Time [s]')
-ax.set_ylabel(r'Total thermal power [W]')
+ax.set_ylabel(r'Power [%]')
 ax.legend()
 #ax.set_xscale('log')
 #ax.set_yscale('log')

### 2019-09-17 pres/acros.tex
Last paper changes and first presentation commit

--- 2019-06-16 abstract/acros.tex
@@
 \newacronym{ARE}{ARE}{Aircraft Reactor Experiment}
+\newacronym{ARFC}{ARFC}{Advanced Reactors and Fuel Cycles}
 \newacronym{ASME}{ASME}{American Society of Mechanical Engineers}
@@
 \newacronym{BIDS}{BIDS}{Berkeley Institute for Data Science}
+\newacronym{BOL}{BOL}{beginning of life}
 \newacronym{CAFCA}{CAFCA}{ Code for Advanced Fuel Cycles Assessment }
@@
 \newacronym{CEA}{CEA}{Commissariat \`a l'\'Energie Atomique et aux \'Energies Alternatives}
-\newacronym{CFD}{CFD}{Computational Fluid Dynamics}
 \newacronym{CI}{CI}{continuous integration}
@@
 \newacronym{CNERG}{CNERG}{Computational Nuclear Engineering Research Group}
-\newacronym{COMSOL}{COMSOL}{COMmon SOLution}
 \newacronym{COSI}{COSI}{Commelini-Sicard}
@@
 \newacronym{DHS}{DHS}{Department of Homeland Security}
-\newacronym{DNP}{DNP}{delayed neutron precursor}
 \newacronym{DOE}{DOE}{Department of Energy}
@@
 \newacronym{EDZ}{EDZ}{Excavation Disturbed Zone}
+\newacronym{EIA}{EIA}{U.S. Energy Information Administration}
+\newacronym{EOL}{EOL}{end of life}
 \newacronym{EPA}{EPA}{Environmental Protection Agency}
 \newacronym{EP}{EP}{Engineering Physics}
-\newacronym{EVOL}{EVOL}{Evaluation and Viability of Liquid Fuel Fast Reactor System}
 \newacronym{FCO}{FCO}{Fuel Cycle Options}
@@
 \newacronym{IEMA}{IEMA}{Illinois Emergency Mangament Agency}
-\newacronym{IHLRWM}{IHLRWM}{International High Level Radioactive Waste Management}
 \newacronym{INL}{INL}{Idaho National Laboratory}
@@
 \newacronym{LWR}{LWR}{Light Water Reactor}
-\newacronym{MAGNOX}{MAGNOX}{Magnesium Alloy Graphie Moderated Gas Cooled Uranium Oxide Reactor}
 \newacronym{MA}{MA}{minor actinide}
@@
 \newacronym{MOOSE}{MOOSE}{Multiphysics Object-Oriented Simulation Environment}
-\newacronym{MOSART}{MOSART}{Molten Salt Actinide Recycler and Transmuter}
 \newacronym{MOX}{MOX}{mixed oxide}
-\newacronym{MPI}{MPI}{Message Passing Interface}
-\newacronym{MRPP}{MRPP}{Multiregion Processing Plant}
 \newacronym{MSBR}{MSBR}{Molten Salt Breeder Reactor}
@@
 \newacronym{NAGRA}{NAGRA}{National Cooperative for the Disposal of Radioactive Waste}
-\newacronym{NEAMS}{NEAMS}{Nuclear Energy Advanced Modeling and Simulation}
+\newacronym{NEAMS}{NEAMS}{Nuclear Engineering Advanced Modeling and Simulation}
 \newacronym{NEUP}{NEUP}{Nuclear Energy University Programs}
@@
 \newacronym{NNSA}{NNSA}{National Nuclear Security Administration}
-\newacronym{NPP}{NPP}{Nuclear Power Plant}
 \newacronym{NPRE}{NPRE}{Department of Nuclear, Plasma, and Radiological Engineering}
@@
 \newacronym{PBFHR}{PB-FHR}{Pebble-Bed Fluoride-Salt-Cooled High-Temperature Reactor}
-\newacronym{PDE}{PDE}{partial differential equation}
 \newacronym{PEI}{PEI}{Peak Environmental Impact}
 \newacronym{PH}{PRONGHORN}{PRONGHORN}
-\newacronym{PRIS}{PRIS}{Power Reactor Information System}
 \newacronym{PRKE}{PRKE}{Point Reactor Kinetics Equations}
@@
 \newacronym{RD}{R\&D}{Research and Development}
-\newacronym{REE}{REE}{rare earth element}
 \newacronym{RELAP}{RELAP}{Reactor Excursion and Leak Analysis Program}
@@
 \newacronym{RIF}{RIF}{Region-Institution-Facility}
-\newacronym{ROD}{ROD}{Reactor Optimum Design}
-\newacronym{SAMOFAR}{SAMOFAR}{Safety Assessment of the Molten Salt Fast Reactor}
-\newacronym{SAM}{SAM}{System Analysis Module}
 \newacronym{SFR}{SFR}{Sodium-Cooled Fast Reactor}
@@
 \newacronym{UFD}{UFD}{Used Fuel Disposition}
+\newacronym{ULOHS}{ULOHS}{Unprotected Loss of Heat Sink}
 \newacronym{UML}{UML}{Unified Modeling Language}
@@
 \newacronym{VISION}{VISION}{the Verifiable Fuel Cycle Simulation Model}
-\newacronym{VVER}{VVER}{Voda-Vodyanoi Energetichesky Reaktor (Russian Pressurized Water Reactor)}
 \newacronym{VV}{V\&V}{verification and validation}

### 2019-09-17 pres/moltres.tex
Last paper changes and first presentation commit

\begin{frame}
	\frametitle{Moltres}
		\textbf{What is Moltres?}
		\begin{itemize}
			\item Moltres is an application code built on the \gls{MOOSE}
			framework, for the simulation of \glspl{MSR}
			\item \gls{MOOSE} is an open source finite element framework that
			relies on Libmesh and PETSc for advanced meshing and PDE solving
			capabilities
			\item Moltres can run transient, implicitly coupled
			neutronics/thermal-hydraulics simulations
			\begin{itemize}
				\item Multi-group neutron diffusion (arbitrary groups)
				\item Delayed neutron precursor decay (with advection)
				\item Incompressible Navier-Stokes for temperature
				advection-diffusion
				\item 1D, 2D, and 3D modeling are supported
			\end{itemize}
		\end{itemize}
\end{frame}

### 2019-09-17 pres/msr.tex
Last paper changes and first presentation commit

\begin{frame}
	\frametitle{Molten Salt Reactors}
		\begin{itemize}
			\item A class of advanced nuclear reactor concepts that contain
			nuclear fuel dissolved and circulating in a molten salt coolant
			loop
			\item May also include designs with solid fuel and molten salt
			coolant
			\item Can potentially run for extended periods with minimal shutdown
			time due to online fuel reprocessing capabilities
		\end{itemize}
		\begin{figure}
			\centering
			\includegraphics[width=.5\textwidth]{./images/msr}
			\caption{Schematic diagram of a general \gls{MSR} concept.}
			\label{fig:msr}
		\end{figure}
\end{frame}

\begin{frame}
	\frametitle{Molten Salt Reactors}
		\textbf{Characteristics and challenges}
		\begin{itemize}
			\item Strong coupling between neutronics and thermal-hydraulics
			\begin{itemize}
				\item Strong Doppler and density feedback in the fuel salt
				\item Relatively more prompt response expected compared to
				existing LWRs
			\end{itemize}
			\item Movement and decay of delayed neutron precursors in the molten
			salt loop
			\begin{itemize}
				\item Conventional safety analysis codes do not account for the
				delayed neutron precursor movement
			\end{itemize}
			\item Constantly evolving fuel composition across the lifetime of an
			\gls{MSR}
			\begin{itemize}
				\item Reactor safety parameters and transient response may be
				different for \gls{BOL} vs \gls{EOL} fuel compositions
			\end{itemize}
		\end{itemize}
\end{frame}

### 2019-09-17 pres/objectives.tex
Last paper changes and first presentation commit

\begin{frame}
	\frametitle{Objectives}
		\textbf{Objectives}
		\begin{itemize}
			\item Verify the neutronics capabilities in Moltres against Serpent
			\item Demonstrate coupled neutronics/thermal-hydraulics simulations
			of the \gls{MSFR} concept,
			\begin{itemize}
				\item with \gls{BOL}, early-life, and \gls{EOL} fuel compositions
				\item for steady state and transient cases: \gls{ULOHS} accident
			\end{itemize}
		\end{itemize}
\end{frame}

### 2019-09-17 data/losca-plotter.py

@@ -66,7 +66,7 @@ ax.plot(tl[1:], heatl[1:] / max(heatl), label=r'Early-life')
 ax.plot(tq[1:], heatq[1:] / max(heatq), label=r'Equilibrium')
 #ax.plot(ts[1:], heats[1:], label=r'Step')
 ax.set_xlabel(r'Time [s]')
-ax.set_ylabel(r'Power [%]')
+ax.set_ylabel(r'Relative power')
 ax.legend()
 #ax.set_xscale('log')
 #ax.set_yscale('log')

### 2019-09-17 pres/moltres.tex
presentation mid update

@@
 			framework, for the simulation of \glspl{MSR}
-			\item \gls{MOOSE} is an open source finite element framework that
+			\item \gls{MOOSE} is an open source finite element framework written
+			in \texttt{C++} that
 			relies on Libmesh and PETSc for advanced meshing and PDE solving
@@
 				\item Multi-group neutron diffusion (arbitrary groups)
-				\item Delayed neutron precursor decay (with advection)
+				\item \gls{DNP} decay (with advection)
 				\item Incompressible Navier-Stokes for temperature

### 2019-09-17 pres/neutron.tex
presentation mid update

\begin{frame}
	\frametitle{Neutronics Verification}
		\begin{columns}
			\column{5cm}
				\textbf{Serpent Input Parameters}
					\begin{itemize}
						\item 200,000 neutrons per cycle
						\item 50 inactive, 500 active cycles
						\item JEFF-3.1.2 nuclear data library
						\item Six neutron energy groups, eight \gls{DNP} groups
						\item Temperatures defined from 900 K to 1200 K at 50 K
						intervals
					\end{itemize}
			\column{5cm}
				\begin{figure}
					\centering
					\includegraphics[width=\textwidth]
					{../paper/figures/reference}
					\caption{2D axisymmetric model used in Serpent. Derived from
					the \gls{MSFR} reference model
					\cite{fiorina_modelling_2014}.}
					\label{fig:reference}
				\end{figure}
		\end{columns}
\end{frame}

\begin{frame}
	\frametitle{Neutronics Verification}
		\textbf{Fuel Composition Data}
			\begin{itemize}
				\item Depletion calculations performed by Rykhlevskii et
				al. \cite{rykhlevskii_fuel_2019}
				\item 60-year depletion calculation on SCALE/TRITON
				using a unit cell representation of the \gls{MSFR} (and
				three other fast-spectrum \glspl{MSR}
				\item U/Th breeder reprocessing scheme
				\item Compositions:
				\begin{itemize}
					\item Start-up: 77.5\% LiF - 19.9\% ThF$_4$
					- 2.6\% UF$_4$
					\item Early-life: 300 days after start-up
					\item Equilibrium: ~43 years after start-up
					($<$3\% change in TRU vector between depletion
					time-steps)
				\end{itemize}
			\end{itemize}
\end{frame}

\begin{frame}
	\frametitle{Neutronics Verification}
	\begin{columns}
		\column{5cm}
		\textbf{Moltres Simulation Details}
		\begin{itemize}
			\item Adaptive backward Euler time-stepper
			\item Six neutron groups, eight \gls{DNP} groups
			\item Vacuum neutron boundary condition on outer surfaces
			\item Uniform upward flow of 1.125 m s$^{-1}$
			\item Flow/decay of \glspl{DNP} and heat removal in the outer loop
			is simulated on a simplified 1D geometry separate from active core
			region
			\item Fixed heat removal rate to secondary loop system
		\end{itemize}
		\column{5cm}
		\begin{figure}
			\centering
			\includegraphics[width=.8\textwidth]{../paper/figures/mesh}
			\caption{Mesh of the 2D axisymmetric model used in Moltres. The
			grey and red regions represent the fuel and blanket salt
			respectively.}
			\label{fig:mesh}
		\end{figure}
	\end{columns}
\end{frame}

\begin{frame}
	\frametitle{Neutronics Verification}
		\textbf{Results}
			\begin{figure}
				\centering
				\includegraphics[width=.8\textwidth]{../paper/figures/nt-spec}
				\caption{Fine-group and six-group neutron flux distributions
				from Serpent and Moltres (start-up composition without \gls{DNP}
				drift).}
				\label{fig:ntspec}
			\end{figure}
\end{frame}

### 2019-09-19 pres/conclusion.tex
presentation slides first draft

\begin{frame}
	\frametitle{Conclusion}
		The neutron group fluxes and reactivity coefficients from Moltres
		(without \gls{DNP} drift) are in
		good agreement with Serpent results, in the context of the \gls{MSFR}.

		\vspace{.3cm}
		The steady state neutron flux, temperature, and \gls{DNP} distributions
		observed are expected for uniform flow.

		\vspace{.3cm}
		Discrepancies in peak neutron
		flux and temperature distributions to other work are primarily due to
		the minor differences in core geometry and using uniform flow instead of
		appling a turbulence model.

		\vspace{.3cm}
		Higher core temperatures observed for start-up fuel composition than
		early-life and equilibrium compositions.

		\vspace{.3cm}
		Discrepancy in average core temperatures during \gls{ULOHS} is mainly due
		to the lack of a decay heat model in Moltres.
\end{frame}

### 2019-09-19 pres/msr.tex
presentation mid update
presentation slides first draft

@@
 			\end{itemize}
-			\item Movement and decay of delayed neutron precursors in the molten
+			\item Movement and decay of \gls{DNP} in the molten
 			salt loop
@@
 				\item Reactor safety parameters and transient response may be
-				different for \gls{BOL} vs \gls{EOL} fuel compositions
+				different for start-up vs equilibrium fuel compositions
 			\end{itemize}

### 2019-09-19 pres/neutron.tex
presentation slides first draft

@@
 	\begin{columns}
-		\column{5cm}
+		\column{5.5cm}
 		\textbf{Moltres Simulation Details}
 		\begin{itemize}
+			\small
 			\item Adaptive backward Euler time-stepper
 			\item Six neutron groups, eight \gls{DNP} groups
-			\item Vacuum neutron boundary condition on outer surfaces
+			\item Vacuum neutron boundary condition on outer edges
 			\item Uniform upward flow of 1.125 m s$^{-1}$
@@
 		\end{itemize}
-		\column{5cm}
+		\column{4.5cm}
 		\begin{figure}
 			\centering
-			\includegraphics[width=.8\textwidth]{../paper/figures/mesh}
+			\includegraphics[width=.9\textwidth]{../paper/figures/mesh}
 			\caption{Mesh of the 2D axisymmetric model used in Moltres. The
@@
 				from Serpent and Moltres (start-up composition without \gls{DNP}
-				drift).}
+				drift at 973 K).}
 				\label{fig:ntspec}
@@
 \end{frame}
+
+\begin{frame}
+	\frametitle{Neutronics Verification}
+		\textbf{Temperature Reactivity Feedback}
+			\begin{table}[t]
+				\centering
+				\caption{Temperature reactivity feedback coefficients.}
+				\begin{tabular}{lccc}
+					\hline
+					\multirow{2}{*}{Composition} & {$\alpha_T$ [pcm K$^{-1}$]} & {$\alpha_T$ [pcm K$^{-1}$]} & Difference\\
+					& Serpent & Moltres & [pcm K$^{-1}$]\\
+					\hline
+					Start-up & $-7.39 \pm 0.03$ & $-7.46$ & $-0.07$\\
+					Early-life & $-7.25 \pm 0.03$ & $-7.33$ & $-0.08$\\
+					Equilibrium & $-6.24 \pm 0.03$ & $-6.34$ & $-0.10$\\
+					\hline
+				\end{tabular}
+				\label{table:reactivity}
+			\end{table}	
+\end{frame}

### 2019-09-19 pres/ulohs.tex
presentation slides first draft

\begin{frame}
	\frametitle{Unprotected Loss of Heat Sink}
		\textbf{Problem Description}
			\begin{itemize}
				\item \gls{ULOHS} accidents generally occur due to various causes
				of failure in the heat exchanger or secondary coolant loop
				\item In this work, \gls{ULOHS} is simulated by an exponential
				decrease in the heat loss rate from the heat exchanger with a
				time constant of 5 s
				\item Expect to observe a rise in temperature, accompanied by a
				decrease in neutron flux and heat generation
			\end{itemize}
\end{frame}

\begin{frame}
	\frametitle{Unprotected Loss of Heat Sink}
		\textbf{Results}
		\begin{columns}
			\column{5cm}
			\begin{figure}
				\centering
				\includegraphics[width=\textwidth]{../paper/figures/loscatemp}
				\caption{Rise in average core temperature during \gls{ULOHS}}
			\end{figure}
			\column{5cm}
			\begin{figure}
				\centering
				\includegraphics[width=\textwidth]{../paper/figures/loscaheat}
				\caption{Power generation during \gls{ULOHS}}
			\end{figure}
		\end{columns}
		\begin{itemize}
			\item \gls{ULOHS} starts at t = 0
			\item Average fuel temperature in core stabilizes at 10 K higher than
			the initial temperature
			\item Lower than expected temperature increase as decay heat is not
			modeled
		\end{itemize}
\end{frame}

### 2019-10-12 pres/acks.tex
Final version

\begin{frame}
	\frametitle{Acknowledgments}
    	Sun Myung Park is supported by the Singapore Nuclear Research and Safety
    	Initiative (SNRSI) Postgraduate Scholarship.

    	\vspace{.3cm}
    	Andrei Rykhlevskii and Dr Kathryn Huff are both supported by funding from
    	the DOE ARPA-E MEITNER Program (award DE-AR0000983).

    	\vspace{.3cm}
    	Dr Kathryn Huff is also supported by the Blue Waters sustained-petascale
    	computing project supported by the National Science Foundation.
\end{frame}

\begin{frame}
	\large
	\centering
	\textbf{Thank you for your attention!}
\end{frame}

### 2019-10-12 pres/conclusion.tex
Final version

@@
 		(without \gls{DNP} drift) are in
-		good agreement with Serpent results, in the context of the \gls{MSFR}.
+		good agreement with Serpent results.
 
@@
 		\vspace{.3cm}
-		Discrepancies in peak neutron
-		flux and temperature distributions to other work are primarily due to
-		the minor differences in core geometry and using uniform flow instead of
-		appling a turbulence model.
+		Discrepancies present in peak neutron
+		flux and temperature distributions relative to other work
 
@@
 		early-life and equilibrium compositions.
-
-		\vspace{.3cm}
-		Discrepancy in average core temperatures during \gls{ULOHS} is mainly due
-		to the lack of a decay heat model in Moltres.
 \end{frame}

### 2019-10-12 pres/moltres.tex
Final version

@@
 		\begin{itemize}
-			\item Moltres is an application code built on the \gls{MOOSE}
-			framework, for the simulation of \glspl{MSR}
-			\item \gls{MOOSE} is an open source finite element framework written
-			in \texttt{C++} that
+			\item Moltres \cite{lindsay_introduction_2018} is an application
+			built on the \gls{MOOSE} framework, for the simulation of \glspl{MSR}
+			\item \gls{MOOSE} \cite{gaston_moose:_2009} is an open source finite
+			element framework written in \texttt{C++} that
 			relies on Libmesh and PETSc for advanced meshing and PDE solving
@@
 			\begin{itemize}
-				\item Multi-group neutron diffusion (arbitrary groups)
+				\item Multi-group neutron diffusion (arbitrary no. of groups)
 				\item \gls{DNP} decay (with advection)

### 2019-10-12 pres/neutron.tex
Final version

--- 2019-09-17 pres/neutron.tex
@@
 \begin{frame}
-	\frametitle{Neutronics Verification}
+	\frametitle{Neutronics Results}
 		\begin{columns}
@@
 					\begin{itemize}
+						\item Neutron population
+							\begin{itemize}
 								\item 200,000 neutrons per cycle
 								\item 50 inactive, 500 active cycles
+								\item 5 pcm statistical error in $k_{eff}$
+							\end{itemize}
 						\item JEFF-3.1.2 nuclear data library
-						\item Six neutron energy groups, eight \gls{DNP} groups
+						\item Six neutron energy groups
+						\item Eight delayed neutron precursor groups
 						\item Temperatures defined from 900 K to 1200 K at 50 K
@@
 					\end{itemize}
-			\column{5cm}
+			\column{5.5cm}
 				\begin{figure}
@@
 					\includegraphics[width=\textwidth]
-					{../paper/figures/reference}
+					{./images/reference}
 					\caption{2D axisymmetric model used in Serpent. Derived from
 					the \gls{MSFR} reference model
-					\cite{fiorina_modelling_2014}.}
+					\cite{fiorina_modelling_2014}. (Figure not to scale)}
 					\label{fig:reference}
@@
 \begin{frame}
-	\frametitle{Neutronics Verification}
+	\frametitle{Neutronics Results}
 		\textbf{Fuel Composition Data}
 			\begin{itemize}
-				\item Depletion calculations performed by Rykhlevskii et
-				al. \cite{rykhlevskii_fuel_2019}
+				\item Depletion calculations performed in a previous paper by
+				A. Rykhlevskii, B. Betzler, A. Worrall, and K. Huff
+				\cite{rykhlevskii_fuel_2019}
 				\item 60-year depletion calculation on SCALE/TRITON
-				using a unit cell representation of the \gls{MSFR} (and
-				three other fast-spectrum \glspl{MSR}
+				using a unit cell representation of the \gls{MSFR}
 				\item U/Th breeder reprocessing scheme
+				\begin{itemize}
+					\item Th feed, with some $^{233}$U from the blanket rerouted
+					to the fuel salt to maintain criticality
+				\end{itemize}
 				\item Compositions:
 				\begin{itemize}
-					\item Start-up: 77.5\% LiF - 19.9\% ThF$_4$
-					- 2.6\% UF$_4$
+					\item Start-up: LiF - ThF$_4$
+					- UF$_4$ (77.5\% - 19.9\% - 2.6\%)
 					\item Early-life: 300 days after start-up
-					\item Equilibrium: ~43 years after start-up
+					\item Equilibrium: 43 years after start-up
 					($<$3\% change in TRU vector between depletion
@@
 \begin{frame}
-	\frametitle{Neutronics Verification}
+	\frametitle{Neutronics Results}
 	\begin{columns}
-		\column{5cm}
+		\column{5.5cm}
 		\textbf{Moltres Simulation Details}
 		\begin{itemize}
+			\small
 			\item Adaptive backward Euler time-stepper
-			\item Six neutron groups, eight \gls{DNP} groups
-			\item Vacuum neutron boundary condition on outer surfaces
+			\item Six neutron groups
+			\item Eight \gls{DNP} groups
+			\item Vacuum neutron boundary condition on outer edges
 			\item Uniform upward flow of 1.125 m s$^{-1}$
@@
 			region
-			\item Fixed heat removal rate to secondary loop system
+			\item Fixed heat removal rate, $Q_{hx}$, to secondary loop system
 		\end{itemize}
@@
 			\centering
-			\includegraphics[width=.8\textwidth]{../paper/figures/mesh}
-			\caption{Mesh of the 2D axisymmetric model used in Moltres. The
+			\includegraphics[width=\textwidth]{./images/mesh}
+			\caption{\footnotesize Mesh of the 2D axisymmetric model used in
+			Moltres. The
 			grey and red regions represent the fuel and blanket salt
@@
 \begin{frame}
-	\frametitle{Neutronics Verification}
+	\frametitle{Neutronics Results}
 		\textbf{Results}
@@
 				\includegraphics[width=.8\textwidth]{../paper/figures/nt-spec}
-				\caption{Fine-group and six-group neutron flux distributions
-				from Serpent and Moltres (start-up composition without \gls{DNP}
-				drift).}
+				\caption{Continuous and six energy group neutron flux
+				distributions from Serpent and Moltres (start-up composition
+				without \gls{DNP} drift at 973 K).}
 				\label{fig:ntspec}
@@
 \end{frame}
+
+\begin{frame}
+	\frametitle{Neutronics Results}
+		\textbf{Fuel Temperature Reactivity Feedback}
+			\begin{table}[t]
+				\centering
+				\caption{Fuel temperature reactivity feedback coefficients with
+				the start-up fuel composition.}
+				\begin{tabular}{lccc}
+					\hline
+					\multirow{2}{*}{Composition} & {$\alpha_T$ [pcm K$^{-1}$]} & {$\alpha_T$ [pcm K$^{-1}$]} & Difference [\%]\\
+					& Serpent & Moltres & \\
+					\hline
+					Start-up & $-7.39 \pm 0.03$ & $-7.46$ & $-0.94$\\
+					Early-life & $-7.25 \pm 0.03$ & $-7.33$ & $-1.1$\\
+					Equilibrium & $-6.24 \pm 0.03$ & $-6.34$ & $-1.6$\\
+					\hline
+				\end{tabular}
+				\label{table:reactivity}
+			\end{table}	
+\end{frame}

### 2019-10-12 pres/objectives.tex
presentation mid update
presentation slides first draft
Final version

@@
 		\begin{itemize}
-			\item Verify the neutronics capabilities in Moltres against Serpent
+			\item Verify the neutronics results in Moltres against Serpent
+			\cite{leppanen_serpent_2015} with the \gls{MSFR} concept with six
+			neutron energy groups
+			\begin{itemize}
+				\item Previous validation study has been performed with an
+				MSRE-like model with two (fast/thermal) neutron energy groups
+				\cite{lindsay_introduction_2018}
+			\end{itemize}
 			\item Demonstrate coupled neutronics/thermal-hydraulics simulations
-			of the \gls{MSFR} concept,
+			of the \gls{MSFR} concept using Moltres,
 			\begin{itemize}
-				\item with \gls{BOL}, early-life, and \gls{EOL} fuel compositions
+				\item with start-up, early-life, and equilibrium fuel
+				compositions
 				\item for steady state and transient cases: \gls{ULOHS} accident

### 2019-10-12 data/flux-plotter.py

@@ -42,6 +42,7 @@ fig, ax = plt.subplots()
 ax.plot(x[:1000], f[:1000], label=r'Start-up')
 ax.plot(x[:1000], fl[:1000], label=r'Early-life')
 ax.plot(x[:1000], fq[:1000], label=r'Equilibrium')
+ax.plot(0, 8.6e15, label=r'Fiorina et al.', marker='x')
 #ax.plot(ts[1:], gs1[1:], label=r'Step')
 ax.set_xlabel(r'Radius [cm]')
 ax.set_ylabel(r'Total neutron flux [# cm$^{-2}$ s$^{-1}$]')
@@ -69,7 +70,7 @@ ax.plot(x[:1000], g4[:1000], label=r'Group 4')
 ax.plot(x[:1000], g5[:1000], label=r'Group 5')
 ax.plot(x[:1000], g6[:1000], label=r'Group 6')
 #ax.plot(ts[1:], gs1[1:], label=r'Step')
-ax.set_xlabel(r'Radius [m]')
+ax.set_xlabel(r'Radius [cm]')
 ax.set_ylabel(r'Neutron group flux [# cm$^{-2}$ s$^{-1}$]')
 ax.legend()
 plt.savefig('stflux.png', dpi=400)

### 2019-10-12 data/losca-plotter.py

@@ -61,12 +61,12 @@ ax.legend()
 plt.savefig('loscatemp.png', dpi=400)
 
 fig, ax = plt.subplots()
-ax.plot(t[1:], heat[1:] / max(heat), label=r'Start-up')
-ax.plot(tl[1:], heatl[1:] / max(heatl), label=r'Early-life')
-ax.plot(tq[1:], heatq[1:] / max(heatq), label=r'Equilibrium')
+ax.plot(t[1:], heat[1:] / max(heat) * 100, label=r'Start-up')
+ax.plot(tl[1:], heatl[1:] / max(heatl) * 100, label=r'Early-life')
+ax.plot(tq[1:], heatq[1:] / max(heatq) * 100, label=r'Equilibrium')
 #ax.plot(ts[1:], heats[1:], label=r'Step')
 ax.set_xlabel(r'Time [s]')
-ax.set_ylabel(r'Relative power')
+ax.set_ylabel(r'Power [%]')
 ax.legend()
 #ax.set_xscale('log')
 #ax.set_yscale('log')

### 2019-12-12 paper/paper.tex
Last paper changes and first presentation commit
add conference submission line

@@
 \title{SAFETY ANALYSIS OF THE MOLTEN SALT FAST REACTOR FUEL COMPOSITION USING
-MOLTRES \\~\\~\\~\\}
+MOLTRES \\ \textit{(Preprint submitted to ANS Global 2019 International Fuel
+Cycle Conference)} \\~\\~\\}
 \author{Sun Myung Park$^{a,b}$, Andrei Rykhlevskii$^a$, and
@@
 
-%\begin{center}
-%\section*{Acknowledgements}
-%\end{center}
-
-%Acknowledgements \\
+\begin{center}
+\section*{Acknowledgements}
+\end{center}
+The authors thank members of the \gls{ARFC} group at the University of Illinois
+at Urbana-Champaign for helpful discussions relating to this paper. Sun Myung
+Park is supported by the Singapore Nuclear Research and Safety Initiative
+(SNRSI) Postgraduate Scholarship.
 

### 2021-03-15 data/losca-plotter.py
Revert "Swap wrong plot"
This reverts commit e985f987bf2693439eff9b755835e3ca5b39fcba.

@@ -14,7 +14,7 @@ temp = df['temp_fuel']
 heat = df['heat']
 #maxe = df['max_temp_fuel']
 
-dfl = pd.read_csv('ulohs-st-prec_out.csv')
+dfl = pd.read_csv('losca-el_out.csv')
 tl = dfl['time']
 g1l = dfl['group1_current']
 g2l = dfl['group2_current']

### 2021-03-15 pres/msr.tex

@@
 			\begin{itemize}
-				\item Strong Doppler and density feedback in the fuel salt
-				\item Relatively more prompt response expected compared to
+				\item Strong density feedback in the fuel salt
+				\item Stronger prompt response expected compared to
 				existing LWRs
 			\end{itemize}
-			\item Movement and decay of \gls{DNP} in the molten
+			\item Movement of \glspl{DNP} in the molten
 			salt loop
@@
 			\begin{itemize}
-				\item Reactor safety parameters and transient response may be
-				different for start-up vs equilibrium fuel compositions
+				\item Reactor safety parameters and transient response may
+				change over time from start-up to equilibrium compositions
 			\end{itemize}

### 2021-03-15 pres/ulohs.tex

@@
 			\begin{itemize}
-				\item \gls{ULOHS} accidents generally occur due to various causes
-				of failure in the heat exchanger or secondary coolant loop
+				\item \gls{ULOHS} accidents are imagined to occur due to various
+				causes of failure in the heat exchanger or secondary coolant
+				loop with no safety response (e.g. scram)
 				\item In this work, \gls{ULOHS} is simulated by an exponential
@@
 				time constant of 5 s
+					\begin{align*}
+						Q_{hx} = Q_{hx,0} e^{-t/5}
+					\end{align*}
 				\item Expect to observe a rise in temperature, accompanied by a
@@
 		\begin{columns}
-			\column{5cm}
+			\column[t]{5.5cm}
 			\begin{figure}
@@
 			\end{figure}
-			\column{5cm}
+			\column[t]{5.5cm}
 			\begin{figure}
 				\centering
-				\includegraphics[width=\textwidth]{../paper/figures/loscaheat}
+				\includegraphics[width=\textwidth]{./images/loscaheat}
 				\caption{Power generation during \gls{ULOHS}}
@@
 			the initial temperature
-			\item Lower than expected temperature increase as decay heat is not
-			modeled
+			\item Lower than expected temperature increase compared to Fiorina
+			et al. \cite{fiorina_investigation_2013}
 		\end{itemize}
